---
title: "Clustering"
author: "Connor Flynn"
date: "7/6/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(readxl)
library(xlsx)
library(ClustImpute)
library(tidyverse)
library(cluster)
library(factoextra)
library(gridExtra)
library(corrplot)
library(janitor)
options(scipen = 99)
options(ggrepel.max.overlaps = Inf)
```

Read In Data

```{r}
sdg_indicators <- read_csv(here("data/sdg_data/sdg_indicators.csv"))
```

Remove Singapore

```{r}
sdg_indicators <- sdg_indicators %>% 
  filter(GeoAreaName != "Singapore")
```

Convert values of first row to row names

```{r}
sdg_indicators <- sdg_indicators %>% 
  remove_rownames %>% 
  column_to_rownames(var="GeoAreaName")
```



Only select columns where certain % of rows have values that are not NA

```{r}
sdg_indicators_less_na <- sdg_indicators[, which(colMeans(!is.na(sdg_indicators)) > 0.45)]
```

ClustImpute



run ClustImpute function to receive ClustImpute object

```{r}
res <- ClustImpute(sdg_indicators_less_na, nr_cluster = 3)
```

within ClustImpute object, scale the imputed data

```{r}
res_complete_data <- res$complete_data
# res_complete_data_scaled <- scale(res$complete_data)
```

Remove columns with 0 variance

```{r}
res_complete_data_no_variance <- res_complete_data[, sapply(res_complete_data, var) != 0]
```

create visualization to decide appropriate \# of clusters for kmeans function

```{r}
fviz_nbclust(res_complete_data_no_variance, kmeans, method = "wss")
```

```{r}
set.seed(123)
kmeans2 <- kmeans(res_complete_data_no_variance, center = 3, nstart = 100)
```

```{r}
fviz_cluster(kmeans2, data = res_complete_data_no_variance,
geom = c("text","point"),
             repel = TRUE,            # Avoid label overlapping
             show.clust.cent = TRUE, # Show cluster centers
             palette = "lancet",         # Color palette see ?ggpubr::ggpar
             ggtheme = theme_bw()+
              theme(axis.text.x = element_text( hjust = 0.5, vjust = 0.5, size=15),
        axis.title.x =element_text(size=20),
        axis.text.y = element_text(hjust = 0.5, vjust = 0.5, size=15),
        axis.title.y =element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.text = element_text(size=25)))
```

```{r}
sil <- silhouette(kmeans2$cluster, dist(res_complete_data_no_variance))
fviz_silhouette(sil)
```


Cluster Goal 1


```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```

Convert Value Column to class numeric
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal1_tidy_grouped <- goal1 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal1_wider <- goal1_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```


```{r}
goal1_wider <- goal1_wider %>% 
  filter(GeoAreaName != "Cuba",
         GeoAreaName != "Singapore")
```




```{r}
goal1_wider <- goal1_wider %>% 
  remove_rownames %>% 
  column_to_rownames(var="GeoAreaName")
```


```{r}
goal1_less_na <- goal1_wider[, which(colMeans(!is.na(goal1_wider)) > 0.45)]
```


```{r}
res1 <- ClustImpute(goal1_less_na, nr_cluster = 3)
```

```{r}
res1_complete_data <- res1$complete_data
```

```{r}
fviz_nbclust(res1_complete_data, kmeans, method = "wss")
```

```{r}
set.seed(123)
kmeans1 <- kmeans(res1_complete_data, center = 4, nstart = 100)
```


```{r}
fviz_cluster(kmeans1, data = res1_complete_data)
```


Bar 

```{r}
goal1_wider_clean <- clean_names(goal1_wider)
```

```{r}
ggplot(data = goal1_wider_clean, aes(y = rownames(goal1_wider_clean), x =  proportion_of_population_below_international_poverty_line_percent)) +
  geom_col()
```
```{r}
res1_complete_data_clean <- clean_names(res1_complete_data)
```


```{r}
write_csv(res_complete_data, here("data/sdg_data/clust_impute_all_indicators"))
```



```{r}
ggplot(data = res1_complete_data_clean, aes(y = rownames(res1_complete_data_clean), 
                                            x =  proportion_of_population_below_international_poverty_line_percent,
                                            fill = rownames(res1_complete_data_clean))) +
  geom_col(show.legend = FALSE) + 
  scale_fill_manual(values = c(Anguilla                         = "blue",  
                               Belize                     = "blue",
                               "Cook Islands"                     = "blue",       
                               Palau = "blue",
                               "Puerto Rico"                      = "blue",   
                               Suriname              = "blue",
                              " Trinidad and Tobago"     = "blue",
                               "United States Virgin Islands" = "blue",
                               Aruba                          = "blue",
                               Bahamas                         = "blue",
                               Barbados           = "blue",
                               "British Virgin Islands" = "blue",
                               Dominica                         = "blue", 
                               Grenada                          = "blue", 
                               Guyana = "blue",
                               "Saint Vincent and the Grenadines"= "blue",
                               "Antigua and Barbuda"            = "blue",
                               "Saint Kitts and Nevis"            = "blue",              
                               Curaçao                    = "blue",
                              " New Caledonia" = "blue",
                               "Sint Maarten (Dutch part) "       = "blue",           
                               "American Samoa"                 = "blue",
                               "French Polynesia"                 = "blue",            
                               Guam = "blue",
                               Niue         = "blue",
                               "Northern Mariana Islands"         = "blue",              
                               Montserrat = "blue"))
```
```{r}
goal1_wider_clean_na <- goal1_wider_clean %>% 
  filter(is.na(proportion_of_population_below_international_poverty_line_percent))
```



```{r}
res_complete_data_clean <- clean_names(res_complete_data)
```

```{r}
ggplot(data = res_complete_data_clean, aes(y = rownames(res_complete_data_clean), 
                                            x =  proportion_of_population_below_international_poverty_line_percent,
                                            fill = rownames(res_complete_data_clean))) +
  geom_col(show.legend = FALSE) + 
  scale_fill_manual(values = c(Anguilla                         = "blue",  
                               Belize                     = "blue",
                               "Cook Islands"                     = "blue",       
                               Palau = "blue",
                               "Puerto Rico"                      = "blue",   
                               Suriname              = "blue",
                              " Trinidad and Tobago"     = "blue",
                               "United States Virgin Islands" = "blue",
                               Aruba                          = "blue",
                               Bahamas                         = "blue",
                               Barbados           = "blue",
                               "British Virgin Islands" = "blue",
                               Dominica                         = "blue", 
                               Grenada                          = "blue", 
                               Guyana = "blue",
                               "Saint Vincent and the Grenadines"= "blue",
                               "Antigua and Barbuda"            = "blue",
                               "Saint Kitts and Nevis"            = "blue",              
                               Curaçao                    = "blue",
                              " New Caledonia" = "blue",
                               "Sint Maarten (Dutch part) "       = "blue",           
                               "American Samoa"                 = "blue",
                               "French Polynesia"                 = "blue",            
                               Guam = "blue",
                               Niue         = "blue",
                               "Northern Mariana Islands"         = "blue",              
                               Montserrat = "blue"))
```

