---
title: "import_tidy_join"
author: "Connor Flynn"
date: "6/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(readxl)
library(xlsx)
library(ClustImpute)
library(tidyverse)
library(cluster)
library(factoextra)
library(gridExtra)
options(scipen = 99)
```

Goal 1


Import data
```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```

Convert Value Column to class numeric
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal1$Value[is.nan(goal1$Value)]<-NA
```




```{r}
goal1$GeoAreaName <- gsub(" ", "_", goal1$GeoAreaName)

goal1$SeriesDescription <- gsub(" ", "_", goal1$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal1_tidy_grouped <- goal1 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal1_wider <- goal1_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```



```{r}
goal1_wider <- goal1_wider %>% 
  clean_names()
```

Goal 2


Import data
```{r}
goal2 <- read_csv(here("data/sdg_data/Goal2.csv"))

```

Convert Value Column to class numeric
```{r}
goal2 <- goal2 %>% 
  mutate(Value = as.numeric(Value))
```
```{r}
goal2$Value[is.nan(goal2$Value)]<-NA
```


```{r}
goal2$GeoAreaName <- gsub(" ", "_", goal2$GeoAreaName)

goal2$SeriesDescription <- gsub(" ", "_", goal2$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}
goal2_tidy_grouped <- goal2 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal2_wider <- goal2_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal2_wider <- goal2_wider  %>% 
  filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```


```{r}
goal2_wider <- goal2_wider %>% 
  clean_names()
```




```{r}
goals_1_2_joined <- full_join(goal1_wider, goal2_wider, by = "geo_area_name")
```

Goal 3 

Import data
```{r}
goal3 <- read_csv(here("data/sdg_data/Goal3.csv"))

```

Convert Value Column to class numeric
```{r}
goal3 <- goal3 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal3$Value[is.nan(goal3$Value)]<-NA
```


```{r}
goal3$GeoAreaName <- gsub(" ", "_", goal3$GeoAreaName)

goal3$SeriesDescription <- gsub(" ", "_", goal3$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal3_tidy_grouped <- goal3 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal3_wider <- goal3_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```



```{r}
goal3_wider <- goal3_wider %>% 
  clean_names()
```



```{r}
goals_1_2_3_joined <- full_join(goals_1_2_joined, goal3_wider, by = "geo_area_name")
```


Goal 4

Import data
```{r}
goal4 <- read_csv(here("data/sdg_data/Goal4.csv"))

```

Convert Value Column to class numeric
```{r}
goal4 <- goal4 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal4$Value[is.nan(goal4$Value)]<-NA
```


```{r}
goal4$GeoAreaName <- gsub(" ", "_", goal4$GeoAreaName)

goal4$SeriesDescription <- gsub(" ", "_", goal4$SeriesDescription)
```



Group in order to get median value form multiple years/categories of data
```{r}

goal4_tidy_grouped <- goal4 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal4_wider <- goal4_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue) 

goal4_wider <- goal4_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```



```{r}
goal4_wider <- goal4_wider %>% 
  clean_names()
```



```{r}
goals_1_2_3_4_joined <- full_join(goals_1_2_3_joined, goal4_wider, by = "geo_area_name")
```


Goal 5

Import data
```{r}
goal5 <- read_csv(here("data/sdg_data/Goal5.csv"))

```

Convert Value Column to class numeric
```{r}
goal5 <- goal5 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal5$Value[is.nan(goal5$Value)]<-NA
```

```{r}
goal5$GeoAreaName <- gsub(" ", "_", goal5$GeoAreaName)

goal5$SeriesDescription <- gsub(" ", "_", goal5$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal5_tidy_grouped <- goal5 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal5_wider <- goal5_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal5_wider <- goal5_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```


```{r}
goal5_wider <- goal5_wider %>% 
  clean_names()
```



```{r}
goals_1_2_3_4_5_joined <- full_join(goals_1_2_3_4_joined, goal5_wider, by = "geo_area_name")
```


Goal 6

Import data
```{r}
goal6 <- read_csv(here("data/sdg_data/Goal6.csv"))

```

Convert Value Column to class numeric
```{r}
goal6 <- goal6 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal6$Value[is.nan(goal6$Value)]<-NA
```



```{r}
goal6$GeoAreaName <- gsub(" ", "_", goal6$GeoAreaName)

goal6$SeriesDescription <- gsub(" ", "_", goal6$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal6_tidy_grouped <- goal6 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal6_wider <- goal6_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal6_wider <- goal6_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```



```{r}
goal6_wider <- goal6_wider %>% 
  clean_names()
```


```{r}
goals_1_2_3_4_5_6_joined <- full_join(goals_1_2_3_4_5_joined, goal6_wider, by = "geo_area_name")
```


Goal 7

Import data
```{r}
goal7 <- read_csv(here("data/sdg_data/Goal7.csv"))

```

Convert Value Column to class numeric
```{r}
goal7 <- goal7 %>% 
  mutate(Value = as.numeric(Value))

```


```{r}
goal7$Value[is.nan(goal7$Value)]<-NA
```


```{r}
goal7$GeoAreaName <- gsub(" ", "_", goal7$GeoAreaName)

goal7$SeriesDescription <- gsub(" ", "_", goal7$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal7_tidy_grouped <- goal7 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal7_wider <- goal7_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal7_wider <- goal7_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```



```{r}
goal7_wider <- goal7_wider %>% 
  clean_names()
```


```{r}
goals_1_2_3_4_5_6_7_joined <- full_join(goals_1_2_3_4_5_6_joined, goal7_wider, by = "geo_area_name")
```


Goal 8 

Import data
```{r}
goal8 <- read_csv(here("data/sdg_data/Goal8.csv"))

```

Convert Value Column to class numeric
```{r}
goal8 <- goal8 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal8$Value[is.nan(goal8$Value)]<-NA
```


```{r}
goal8$GeoAreaName <- gsub(" ", "_", goal8$GeoAreaName)

goal8$SeriesDescription <- gsub(" ", "_", goal8$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal8_tidy_grouped <- goal8 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal8_wider <- goal8_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```



```{r}
goal8_wider <- goal8_wider %>% 
  clean_names()
```



```{r}
goals_1_2_3_4_5_6_7_8_joined <- full_join(goals_1_2_3_4_5_6_7_joined, goal8_wider, by = "geo_area_name")
```



Goal 9

Import data
```{r}
goal9 <- read_csv(here("data/sdg_data/Goal9.csv"))

```

Convert Value Column to class numeric
```{r}
goal9 <- goal9 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal9$Value[is.nan(goal9$Value)]<-NA
```


```{r}
goal9$GeoAreaName <- gsub(" ", "_", goal9$GeoAreaName)

goal9$SeriesDescription <- gsub(" ", "_", goal9$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal9_tidy_grouped <- goal9 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```




```{r}
goal9_wider <- goal9_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal9_wider <- goal9_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```



```{r}
goal9_wider <- goal9_wider %>% 
  clean_names()
```


```{r}
goals_1_2_3_4_5_6_7_8_9_joined <- full_join(goals_1_2_3_4_5_6_7_8_joined, goal9_wider, by = "geo_area_name")
```


Goal 10

Import data
```{r}
goal10 <- read_csv(here("data/sdg_data/Goal10.csv"))

```

Convert Value Column to class numeric
```{r}
goal10 <- goal10 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal10$Value[is.nan(goal10$Value)]<-NA
```

```{r}
goal10$GeoAreaName <- gsub(" ", "_", goal10$GeoAreaName)

goal10$SeriesDescription <- gsub(" ", "_", goal10$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal10_tidy_grouped <- goal10 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal10_wider <- goal10_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal10_wider <- goal10_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```



```{r}
goal10_wider <- goal10_wider %>% 
  clean_names()
```



```{r}
goals_1_2_3_4_5_6_7_8_9_10_joined <- full_join(goals_1_2_3_4_5_6_7_8_9_joined, goal10_wider, by = "geo_area_name")
```

Removing NA's

```{r}
sdg_1_10 <- goals_1_2_3_4_5_6_7_8_9_10_joined

sdg_1_10 <- sdg_1_10 %>%
  filter(#GeoAreaName != "Singapore",
         geo_area_name != "Small_island_developing_States_(SIDS)")
```


```{r}
sdg_1_10_less_na <- sdg_1_10[, which(colMeans(!is.na(sdg_1_10)) > 0.1)]
```




Goal 11


Import data
```{r}
goal11 <- read_csv(here("data/sdg_data/Goal11.csv"))

```

Convert Value Column to class numeric
```{r}
goal11 <- goal11 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal11$Value[is.nan(goal11$Value)]<-NA
```

```{r}
goal11$GeoAreaName <- gsub(" ", "_", goal11$GeoAreaName)

goal11$SeriesDescription <- gsub(" ", "_", goal11$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal11_tidy_grouped <- goal11 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal11_wider <- goal11_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal11_wider <- goal11_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba")
```


```{r}
goal11_wider <- goal11_wider %>% 
  clean_names()
```




```{r}
sdg_1_11_joined <- full_join(sdg_1_10, goal11_wider, by = "geo_area_name")
```



Goal 12 

Import data
```{r}
goal12 <- read_csv(here("data/sdg_data/Goal12.csv"))

```

Convert Value Column to class numeric
```{r}
goal12 <- goal12 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal12$Value[is.nan(goal12$Value)]<-NA
```


```{r}
goal12$GeoAreaName <- gsub(" ", "_", goal12$GeoAreaName)

goal12$SeriesDescription <- gsub(" ", "_", goal12$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal12_tidy_grouped <- goal12 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal12_wider <- goal12_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal12_wider <- goal12_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba",
           GeoAreaName != "Small_island_developing_States_(SIDS)")
```



```{r}
goal12_wider <- goal12_wider %>% 
  clean_names()
```




```{r}
sdg_1_12_joined <- full_join(sdg_1_11_joined, goal12_wider, by = "geo_area_name" )
```




Goal 13

Import data
```{r}
goal13 <- read_csv(here("data/sdg_data/Goal13.csv"))

```

Convert Value Column to class numeric
```{r}
goal13 <- goal13 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal13$Value[is.nan(goal13$Value)]<-NA
```


```{r}
goal13$GeoAreaName <- gsub(" ", "_", goal13$GeoAreaName)

goal13$SeriesDescription <- gsub(" ", "_", goal13$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal13_tidy_grouped <- goal13 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal13_wider <- goal13_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal13_wider <- goal13_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba",
           GeoAreaName != "Small_island_developing_States_(SIDS)")
```



```{r}
goal13_wider <- goal13_wider %>% 
  clean_names()
```



```{r}
sdg_1_13_joined <- full_join(sdg_1_12_joined, goal13_wider, by = "geo_area_name")
```



Goal 14

Import data
```{r}
goal14 <- read_csv(here("data/sdg_data/Goal14.csv"))

```

Convert Value Column to class numeric
```{r}
goal14 <- goal14 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal14$Value[is.nan(goal14$Value)]<-NA
```

```{r}
goal14$GeoAreaName <- gsub(" ", "_", goal14$GeoAreaName)

goal14$SeriesDescription <- gsub(" ", "_", goal14$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal14_tidy_grouped <- goal14 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal14_wider <- goal14_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal14_wider <- goal14_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba",
           GeoAreaName != "Small_island_developing_States_(SIDS)")
```



```{r}
goal14_wider <- goal14_wider %>% 
  clean_names()
```



```{r}
sdg_1_14_joined <- full_join(sdg_1_13_joined, goal14_wider, by = "geo_area_name")
```



Goal 15 

Import data
```{r}
goal15 <- read_csv(here("data/sdg_data/Goal15.csv"))

```

Convert Value Column to class numeric
```{r}
goal15 <- goal15 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal15$Value[is.nan(goal15$Value)]<-NA
```


```{r}
goal15$GeoAreaName <- gsub(" ", "_", goal15$GeoAreaName)

goal15$SeriesDescription <- gsub(" ", "_", goal15$SeriesDescription)
```



Group in order to get median value form multiple years/categories of data
```{r}

goal15_tidy_grouped <- goal15 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal15_wider <- goal15_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal15_wider <- goal15_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba",
           GeoAreaName != "Small_island_developing_States_(SIDS)")
```



```{r}
goal15_wider <- goal15_wider %>% 
  clean_names()
```




```{r}
sdg_1_15_joined <- full_join(sdg_1_14_joined, goal15_wider, by = "geo_area_name")
```


Goal 16 

Import data
```{r}
goal16 <- read_csv(here("data/sdg_data/Goal16.csv"))

```

Convert Value Column to class numeric
```{r}
goal16 <- goal16 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal16$Value[is.nan(goal16$Value)]<-NA
```


```{r}
goal16$GeoAreaName <- gsub(" ", "_", goal16$GeoAreaName)

goal16$SeriesDescription <- gsub(" ", "_", goal16$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal16_tidy_grouped <- goal16 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal16_wider <- goal16_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal16_wider <- goal16_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba",
           GeoAreaName != "Small_island_developing_States_(SIDS)")
```



```{r}
goal16_wider <- goal16_wider %>% 
  clean_names()
```




```{r}
sdg_1_16_joined <- full_join(sdg_1_15_joined, goal16_wider, by = "geo_area_name")
```



Goal 17 


Import data
```{r}
goal17 <- read_csv(here("data/sdg_data/Goal17.csv"))

```

Convert Value Column to class numeric
```{r}
goal17 <- goal17 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal17$Value[is.nan(goal17$Value)]<-NA
```


```{r}
goal17$GeoAreaName <- gsub(" ", "_", goal17$GeoAreaName)

goal17$SeriesDescription <- gsub(" ", "_", goal17$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal17_tidy_grouped <- goal17 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```




```{r}
goal17_wider <- goal17_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal17_wider <- goal17_wider %>% 
    filter(GeoAreaName != "Bonaire,_Sint_Eustatius_and_Saba",
           GeoAreaName != "Small_island_developing_States_(SIDS)")
```




```{r}
goal17_wider <- goal17_wider %>% 
  clean_names()
```

```{r}
sdg_1_17_joined <- full_join(sdg_1_16_joined, goal17_wider, by = "geo_area_name") 
```

***Check for duplicates




```{r}
sdg_1_17_joined_duplicate_check <- sdg_1_17_joined[!duplicated(as.list(sdg_1_17_joined))]
```




Write CSV

```{r}
write_csv(sdg_1_17_joined, (here("data/sdg_data/sdg_indicators.csv")))
```





