---
title: "intro_mean_or_median"
author: "Connor Flynn"
date: "7/21/2022"
output: html_document
---

Goal: The goal of this Rmd is to introduce users to the data in it's initial format and show examples of potential biases/flaws in summarizing data



## Load Libraries

The code chunk below reads in packages and functions used in this workflow:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here)

options(scipen = 99)
```


Import data

Each sustainable development goal (sdg) has it's own csv in the 'data' folder. 



Goal 1
```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```


Let's view the first potion of the data frame 

```{r}
head(goal1)
```

This is all the indicator data for Sustainable Development Goal 1 for SIDS.

When we first import the data, we can see:
  - There are multiple observations for one country and the same indicator. 
      - This is to account for differences in data by year, age, sex, and geographic context for the same country.
      - This is a great idea, *however*, an extremely significant amount of the data is NA with this specific scope. 
  - We want a broad picture of sustainable development goal measures for SIDS with as little NA values as possible, so:
      - We we summarize the data by taking the mean or median value of age, sex, year, and urban vs rural geography. 
      - This allows us to have as little NA values as possible, although the number of NA's is still significant, and keep the             data frame to one SIDS per row and one sdg indicator per column.



Make sure the Value column is numeric
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```


Selects columns of interest
```{r}
goal1 <- goal1 %>% 
  select(SeriesDescription, GeoAreaName, Value, TimePeriod, Age, Sex, Location)

head(goal1)
```

Now let's make sure all 52 SIDS are present in the Goal 1 Indicator Measurement

```{r}
unique(goal1$GeoAreaName)
```

How many indicators are in Goal 1

```{r}
unique(goal1$SeriesDescription)
```




Now let's check if all 52 SIDS are present in the Goal 1 Indicator Measurement - for each Indicator

```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)") %>% 
  count(GeoAreaName)
```


Here we see only 24 SIDS have data for the indicator "Proportion of population below international poverty line (%)"

Also, the number of entries for year, age, sex, and geographic context range from:

```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Jamaica")  
 
```

  - Jamaica: 2 entries, a 2002 and 2004 entry for allage, bothsex, allarea


```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Dominican Republic")  
```
 - Dominican Republic: 49 entries
 
 
We have to decide whether to take the *mean or median* to summarize these values so we can end up with one indicator per one sdg indicator data frame

Mean will be more influenced by outliers and the median will be less influenced by outliers
 
 
Let's Use the Dominican Republic and "Proportion of population below international poverty line (%)" as a test
 
 
 
```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Dominican Republic")  %>% 
  summarise(mean_value = mean(Value))
```

```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Dominican Republic")  %>% 
  summarise(median_value = median(Value))
```
 
 
This case is interesting because for this specific indicator it is best to have the most recent year of data, and as the Dominican Republic's population below the international poverty line declines, taking the median seems to give us the most accurate answer.



Let's look at one more country for this indicator 

```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Haiti")  
```

All of the data is for 2012 but ranges from 9 to 38% poverty based on rural vs urban locations

Let's do the mean and median test


```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Haiti")  %>% 
  summarise(mean_value = mean(Value))
```


```{r}
goal1 %>% 
  filter(SeriesDescription == "Proportion of population below international poverty line (%)" &
           GeoAreaName == "Haiti")  %>% 
  summarise(median_value = median(Value))
```





However, Goal 1 also measures the Number of people affected by disaster (number)

For this type of indicator, since storms don't occur every year, taking the most recent year of data is bias. 
Let's look at the data:


```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of people affected by disaster (number)") %>% 
  count(GeoAreaName)
```

37 countries have data on this indicator with a range of 1 to 16 observations per SIDS

Samoa has 12 entries


```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of people affected by disaster (number)" &
           GeoAreaName == "Samoa")
```
 
 
A tsunami hit Samoa on September 29, 2009. On September 29, 2009, two large earthquakes struck midway between Samoa and American Samoa, a U.S. territory. The earthquakes generated tsunami waves of up to 22 meters (72 feet) that engulfed the shores, killing at least 192 people—149 in Samoa, 34 in American Samoa, and 9 in Niuatoputapu, Tonga. 

We want to capture an accurate measurement of natural disasters affecting Samoan residents so let's test mean and median again


```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of people affected by disaster (number)" &
           GeoAreaName == "Samoa") %>% 
  summarise(mean_value = mean(Value))
```
 
```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of people affected by disaster (number)" &
           GeoAreaName == "Samoa") %>% 
  summarise(median_value = median(Value))
```


```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of people affected by disaster (number)" &
           GeoAreaName == "French Polynesia")
```



Lets look at French Polynesia for a similar indicator : "Number of directly affected persons attributed to disasters per 100,000 population (number)" 

```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of directly affected persons attributed to disasters per 100,000 population (number)" &
           GeoAreaName == "French Polynesia") 
```


The value is zero but should be ~ 7 based on the measurement below. It is important to keep data flaws in mind during analysis


```{r}
goal1 %>% 
  filter(SeriesDescription == "Number of deaths due to disaster (number)" &
           GeoAreaName == "French Polynesia") 

```



Lets look at one more Goal 1 Indicator: "[ILO] Proportion of vulnerable population receiving social assistance cash benefit, by sex (%)"

```{r}
goal1 %>% 
  filter(SeriesDescription == "[ILO] Proportion of vulnerable population receiving social assistance cash benefit, by sex (%)") %>% 
  count(GeoAreaName)
```


```{r}
goal1 %>% 
  filter(SeriesDescription == "[ILO] Proportion of vulnerable population receiving social assistance cash benefit, by sex (%)" &
           GeoAreaName == "Cabo Verde") 
```
```{r}
goal1 %>% 
  filter(SeriesDescription == "[ILO] Proportion of vulnerable population receiving social assistance cash benefit, by sex (%)" &
           GeoAreaName == "Guyana") 
```
