---
title: "na heat map"
author: "Connor Flynn"
date: "7/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```


Define Function
```{r}
count_na <- function(x) sum(is.na(x))
```


Goal 1

Import data
```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```

Convert Value Column to class numeric
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal1_tidy_grouped <- goal1 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal1_wider <- goal1_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```

```{r}
goal1_wider_na <- goal1_wider %>% 
  mutate(goal1_na = apply(., 1, count_na))
```

```{r}
goal1_na <- goal1_wider_na %>% 
  select(GeoAreaName, goal1_na)
```



Goal 2 

Import data
```{r}
goal2 <- read_csv(here("data/sdg_data/Goal2.csv"))

```

Convert Value Column to class numeric
```{r}
goal2 <- goal2 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}
goal2_tidy_grouped <- goal2 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal2_wider <- goal2_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal2_wider <- goal2_wider  %>% 
  filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```

```{r}
goal2_wider_na <- goal2_wider %>% 
  mutate(goal2_na = apply(., 1, count_na))
```

```{r}
goal2_na <- goal2_wider_na %>% 
  select(GeoAreaName, goal2_na)
```


Goal 3 

Import data
```{r}
goal3 <- read_csv(here("data/sdg_data/Goal3.csv"))

```

Convert Value Column to class numeric
```{r}
goal3 <- goal3 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal3_tidy_grouped <- goal3 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal3_wider <- goal3_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```


```{r}
goal3_wider_na <- goal3_wider %>% 
  mutate(goal3_na = apply(., 1, count_na))
```

```{r}
goal3_na <- goal3_wider_na %>% 
  select(GeoAreaName, goal3_na)
```


Goal 4

Import data
```{r}
goal4 <- read_csv(here("data/sdg_data/Goal4.csv"))

```

Convert Value Column to class numeric
```{r}
goal4 <- goal4 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal4_tidy_grouped <- goal4 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal4_wider <- goal4_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue) 

goal4_wider <- goal4_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```


```{r}
goal4_wider_na <- goal4_wider %>% 
  mutate(goal4_na = apply(., 1, count_na))
```

```{r}
goal4_na <- goal4_wider_na %>% 
  select(GeoAreaName, goal4_na)
```

Goal 5 

Import data
```{r}
goal5 <- read_csv(here("data/sdg_data/Goal5.csv"))

```

Convert Value Column to class numeric
```{r}
goal5 <- goal5 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal5_tidy_grouped <- goal5 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal5_wider <- goal5_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal5_wider <- goal5_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```

```{r}
goal5_wider_na <- goal5_wider %>% 
  mutate(goal5_na = apply(., 1, count_na))
```

```{r}
goal5_na <- goal5_wider_na %>% 
  select(GeoAreaName, goal5_na)
```


Goal 6

Import data
```{r}
goal6 <- read_csv(here("data/sdg_data/Goal6.csv"))

```

Convert Value Column to class numeric
```{r}
goal6 <- goal6 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal6_tidy_grouped <- goal6 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal6_wider <- goal6_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal6_wider <- goal6_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```


```{r}
goal6_wider_na <- goal6_wider %>% 
  mutate(goal6_na = apply(., 1, count_na))
```

```{r}
goal6_na <- goal6_wider_na %>% 
  select(GeoAreaName, goal6_na)
```


Goal 7 

Import data
```{r}
goal7 <- read_csv(here("data/sdg_data/Goal7.csv"))

```

Convert Value Column to class numeric
```{r}
goal7 <- goal7 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal7_tidy_grouped <- goal7 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal7_wider <- goal7_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal7_wider <- goal7_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```

```{r}
goal7_wider_na <- goal7_wider %>% 
  mutate(goal7_na = apply(., 1, count_na))
```

```{r}
goal7_na <- goal7_wider_na %>% 
  select(GeoAreaName, goal7_na)
```


Goal 8 

Import data
```{r}
goal8 <- read_csv(here("data/sdg_data/Goal8.csv"))

```

Convert Value Column to class numeric
```{r}
goal8 <- goal8 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal8_tidy_grouped <- goal8 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal8_wider <- goal8_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```


```{r}
goal8_wider_na <- goal8_wider %>% 
  mutate(goal8_na = apply(., 1, count_na))
```

```{r}
goal8_na <- goal8_wider_na %>% 
  select(GeoAreaName, goal8_na)
```

Goal 9 

Import data
```{r}
goal9 <- read_csv(here("data/sdg_data/Goal9.csv"))

```

Convert Value Column to class numeric
```{r}
goal9 <- goal9 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal9_tidy_grouped <- goal9 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal9_wider <- goal9_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal9_wider <- goal9_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```


```{r}
goal9_wider_na <- goal9_wider %>% 
  mutate(goal9_na = apply(., 1, count_na))
```

```{r}
goal9_na <- goal9_wider_na %>% 
  select(GeoAreaName, goal9_na)
```


Goal 10 

Import data
```{r}
goal10 <- read_csv(here("data/sdg_data/Goal10.csv"))

```

Convert Value Column to class numeric
```{r}
goal10 <- goal10 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal10_tidy_grouped <- goal10 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal10_wider <- goal10_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal10_wider <- goal10_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```

```{r}
goal10_wider_na <- goal10_wider %>% 
  mutate(goal10_na = apply(., 1, count_na))
```

```{r}
goal10_na <- goal10_wider_na %>% 
  select(GeoAreaName, goal10_na)
```


Goal 11 

Import data
```{r}
goal11 <- read_csv(here("data/sdg_data/Goal11.csv"))

```

Convert Value Column to class numeric
```{r}
goal11 <- goal11 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal11_tidy_grouped <- goal11 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal11_wider <- goal11_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal11_wider <- goal11_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
```

```{r}
goal11_wider_na <- goal11_wider %>% 
  mutate(goal11_na = apply(., 1, count_na))
```

```{r}
goal11_na <- goal11_wider_na %>% 
  select(GeoAreaName, goal11_na)
```


Goal 12

Import data
```{r}
goal12 <- read_csv(here("data/sdg_data/Goal12.csv"))

```

Convert Value Column to class numeric
```{r}
goal12 <- goal12 %>% 
  mutate(Value = as.numeric(Value))
```


Group in order to get median value form multiple years/categories of data
```{r}

goal12_tidy_grouped <- goal12 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value))
```


```{r}
goal12_wider <- goal12_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

goal12_wider <- goal12_wider %>% 
    filter(GeoAreaName != "Bonaire, Sint Eustatius and Saba")
           #GeoAreaName != "Small island developing States (SIDS)")
```


```{r}
goal12_wider_na <- goal12_wider %>% 
  mutate(goal12_na = apply(., 1, count_na))
```

```{r}
goal12_na <- goal12_wider_na %>% 
  select(GeoAreaName, goal12_na)
```

