---
title: "trends"
author: "Connor Flynn"
date: "8/1/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                dplyr,
                missRanger,
                cluster,
                factoextra,
                randomForest,
                plotly,
                kableExtra,
                randomForestExplainer)



options(set.seed(3))
options(scipen = 99)
options(ggrepel.max.overlaps = Inf)
```


Load in Data
```{r}
trends_data <- read_csv(here("data/sdg_data/partial_trends_data.csv"))

sdg_indicators <- read_csv(here("most_recent/data_cleaned_and_summarized/sdg_indicators_joined_most_recent.csv"))
```
Impute sdg indicator data 

*Determine how much data we want to impute
  - Here, I decided that I only want to include columns (indicators) in which at least 40% of the SIDS have data for
```{r}
sdg_indicators_less_na <- sdg_indicators[, which(colMeans(!is.na(sdg_indicators)) > 0.4)]
```



Impute using missRanger function (Random Forest)
```{r}
sdg_indicators_missRanger <- missRanger(sdg_indicators_less_na, 
                                        formula = . ~ ., 
                                        num.trees = 1000,
                                        seed = 3,
                                        returnOOB = TRUE
                                      )
```

Clean to Merge

```{r}
trends_data <- clean_names(trends_data)
```

```{r}
trends_data <- trends_data %>%
     mutate(country = recode(country, 
                            "Bahamas, The" = 'Bahamas',
                             "Micronesia, Fed. Sts." = 	"Micronesia_(Federated_States_of)",
                            "St. Kitts and Nevis" = 	"Saint_Kitts_and_Nevis",
                            	"St. Lucia" = 	"Saint_Lucia", 
                            	"St. Vincent and the Grenadines" = "Saint_Vincent_and_the_Grenadines"
                            
                            ))
```







```{r}
trends_data$country <- gsub(" ", "_", trends_data$country)
```

```{r}
trends_data <- trends_data %>%
  rename(geo_area_name = country)
```


```{r}
trends_data <- trends_data %>%
  select(geo_area_name, 
         goal_1_dash, goal_1_trend, 
         goal_2_dash, goal_2_trend, 
         goal_3_dash, goal_3_trend, 
         goal_4_dash, goal_4_trend, 
         goal_5_dash, goal_5_trend,
         goal_6_dash, goal_6_trend, 
         goal_7_dash, goal_7_trend, 
         goal_8_dash, goal_8_trend,
         goal_9_dash, goal_9_trend, 
         goal_10_dash, goal_10_trend, 
         goal_11_dash, goal_11_trend, 
         goal_12_dash, goal_12_trend, 
         goal_13_dash, goal_13_trend, 
         goal_14_dash, goal_14_trend, 
         goal_15_dash, goal_15_trend, 
         goal_16_dash, goal_16_trend, 
         goal_17_dash, goal_17_trend)
```



```{r}
trends_data_missRanger <- missRanger(trends_data, 
                                        formula = . ~ ., 
                                        num.trees = 1000,
                                        seed = 3,
                                        returnOOB = TRUE
                                      )
```


```{r}
trends_data_missRanger
```


Join

```{r}
sdg_indicators_trends <- left_join(sdg_indicators_missRanger, trends_data_missRanger, by = "geo_area_name")
```


```{r}
sdg_indicators_trends <- sdg_indicators_trends %>%
  remove_rownames %>%
  column_to_rownames(var="geo_area_name")
```


Random Forest

```{r}
sdg_indicators_trends$goal_1_trend <- as.factor(sdg_indicators_trends$goal_1_trend)
```


```{r}
missRanger_rf_goal1_trends <- randomForest(goal_1_trend ~ ., data = sdg_indicators_trends, 
                   importance = TRUE, na.action = "na.omit", )
```


```{r}
missRanger_rf_goal1_trends
```


```{r}
ImpData_missRanger_rf_goal1_trends <- as.data.frame(importance(missRanger_rf_goal1_trends))
ImpData_missRanger_rf_goal1_trends$Var.Names <- row.names(ImpData_missRanger_rf_goal1_trends)



ImpData_missRanger_rf_goal1_trends





ImpData_missRanger_rf_goal1_trends_highest_mse <- ImpData_missRanger_rf_goal1_trends %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal1_trends_highest_mse <- ImpData_missRanger_rf_goal1_trends_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal1_trends_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Goal 2 



```{r}
sdg_indicators_trends$goal_2_trend <- as.factor(sdg_indicators_trends$goal_2_trend)
```


```{r}
missRanger_rf_goal_2_trend <- randomForest(goal_2_trend ~ ., data = sdg_indicators_trends, 
                   importance = TRUE, na.action = "na.omit", )
```


```{r}
missRanger_rf_goal_2_trend
```


```{r}
ImpData_missRanger_rf_goal_2_trend <- as.data.frame(importance(missRanger_rf_goal_2_trend))
ImpData_missRanger_rf_goal_2_trend$Var.Names <- row.names(ImpData_missRanger_rf_goal_2_trend)



ImpData_missRanger_rf_goal_2_trend





ImpData_missRanger_rf_goal_2_trend_highest_mse <- ImpData_missRanger_rf_goal_2_trend %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal_2_trend_highest_mse <- ImpData_missRanger_rf_goal_2_trend_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal_2_trend_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Dash Analysis


```{r}

dash_data <- trends_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```



```{r}
dash_data_sids <- left_join(sdg_indicators, dash_data, by = "geo_area_name")
```

```{r}
dash_data_sids <- dash_data_sids %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```


```{r}
dash_data_sids <- drop_na(dash_data_sids)
```

```{r}
dash_data_sids_missRanger_sdg_indicators <- left_join(dash_data_sids, sdg_indicators_missRanger, by = "geo_area_name")
```



```{r}
dash_data_sids_missRanger_sdg_indicators <- dash_data_sids_missRanger_sdg_indicators %>% 
  remove_rownames %>% 
  column_to_rownames(var="geo_area_name")
```

Random Forest


Goal 1

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_1_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_1_dash)
```


```{r}
missRanger_rf_goal1_dash<- randomForest(goal_1_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal1_dash
```


```{r}
ImpData_missRanger_rf_goal1_dash <- as.data.frame(importance(missRanger_rf_goal1_dash))
ImpData_missRanger_rf_goal1_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal1_dash)



ImpData_missRanger_rf_goal1_dash





ImpData_missRanger_rf_goal1_dash_highest_mse <- ImpData_missRanger_rf_goal1_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal1_dash_highest_mse <- ImpData_missRanger_rf_goal1_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal1_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 2 

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_2_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_2_dash)
```


```{r}
missRanger_rf_goal2_dash<- randomForest(goal_2_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal2_dash
```


```{r}
ImpData_missRanger_rf_goal2_dash <- as.data.frame(importance(missRanger_rf_goal2_dash))
ImpData_missRanger_rf_goal2_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal2_dash)



ImpData_missRanger_rf_goal2_dash





ImpData_missRanger_rf_goal2_dash_highest_mse <- ImpData_missRanger_rf_goal2_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal2_dash_highest_mse <- ImpData_missRanger_rf_goal2_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal2_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```


Goal 3

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_3_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_3_dash)
```


```{r}
missRanger_rf_goal3_dash<- randomForest(goal_3_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal3_dash
```


```{r}
ImpData_missRanger_rf_goal3_dash <- as.data.frame(importance(missRanger_rf_goal3_dash))
ImpData_missRanger_rf_goal3_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal3_dash)



ImpData_missRanger_rf_goal3_dash





ImpData_missRanger_rf_goal3_dash_highest_mse <- ImpData_missRanger_rf_goal3_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal3_dash_highest_mse <- ImpData_missRanger_rf_goal3_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal3_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 4 

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_4_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_4_dash)
```


```{r}
missRanger_rf_goal4_dash<- randomForest(goal_4_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal4_dash
```


```{r}
ImpData_missRanger_rf_goal4_dash <- as.data.frame(importance(missRanger_rf_goal4_dash))
ImpData_missRanger_rf_goal4_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal4_dash)



ImpData_missRanger_rf_goal4_dash





ImpData_missRanger_rf_goal4_dash_highest_mse <- ImpData_missRanger_rf_goal4_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal4_dash_highest_mse <- ImpData_missRanger_rf_goal4_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal4_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 5 



```{r}
dash_data_sids_missRanger_sdg_indicators$goal_5_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_5_dash)
```


```{r}
missRanger_rf_goal5_dash<- randomForest(goal_5_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal5_dash
```


```{r}
ImpData_missRanger_rf_goal5_dash <- as.data.frame(importance(missRanger_rf_goal5_dash))
ImpData_missRanger_rf_goal5_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal5_dash)



ImpData_missRanger_rf_goal5_dash





ImpData_missRanger_rf_goal5_dash_highest_mse <- ImpData_missRanger_rf_goal5_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal5_dash_highest_mse <- ImpData_missRanger_rf_goal5_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal5_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```

Goal 6 

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_6_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_6_dash)
```


```{r}
missRanger_rf_goal6_dash<- randomForest(goal_6_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal6_dash
```


```{r}
ImpData_missRanger_rf_goal6_dash <- as.data.frame(importance(missRanger_rf_goal6_dash))
ImpData_missRanger_rf_goal6_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal6_dash)



ImpData_missRanger_rf_goal6_dash





ImpData_missRanger_rf_goal6_dash_highest_mse <- ImpData_missRanger_rf_goal6_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal6_dash_highest_mse <- ImpData_missRanger_rf_goal6_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal6_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.5) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```





Goal 7 

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_7_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_7_dash)
```


```{r}
missRanger_rf_goal7_dash<- randomForest(goal_7_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal7_dash
```


```{r}
ImpData_missRanger_rf_goal7_dash <- as.data.frame(importance(missRanger_rf_goal7_dash))
ImpData_missRanger_rf_goal7_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal7_dash)



ImpData_missRanger_rf_goal7_dash





ImpData_missRanger_rf_goal7_dash_highest_mse <- ImpData_missRanger_rf_goal7_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal7_dash_highest_mse <- ImpData_missRanger_rf_goal7_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal7_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```


Goal 8 


```{r}
dash_data_sids_missRanger_sdg_indicators$goal_8_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_8_dash)
```


```{r}
missRanger_rf_goal8_dash<- randomForest(goal_8_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal8_dash
```


```{r}
ImpData_missRanger_rf_goal8_dash <- as.data.frame(importance(missRanger_rf_goal8_dash))
ImpData_missRanger_rf_goal8_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal8_dash)



ImpData_missRanger_rf_goal8_dash





ImpData_missRanger_rf_goal8_dash_highest_mse <- ImpData_missRanger_rf_goal8_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal8_dash_highest_mse <- ImpData_missRanger_rf_goal8_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal8_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 9 


```{r}
dash_data_sids_missRanger_sdg_indicators$goal_9_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_9_dash)
```


```{r}
missRanger_rf_goal9_dash<- randomForest(goal_9_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal9_dash
```


```{r}
ImpData_missRanger_rf_goal9_dash <- as.data.frame(importance(missRanger_rf_goal9_dash))
ImpData_missRanger_rf_goal9_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal9_dash)



ImpData_missRanger_rf_goal9_dash





ImpData_missRanger_rf_goal9_dash_highest_mse <- ImpData_missRanger_rf_goal9_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal9_dash_highest_mse <- ImpData_missRanger_rf_goal9_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal9_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Goal 10 

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_10_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_10_dash)
```


```{r}
missRanger_rf_goal10_dash<- randomForest(goal_10_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal10_dash
```


```{r}
ImpData_missRanger_rf_goal10_dash <- as.data.frame(importance(missRanger_rf_goal10_dash))
ImpData_missRanger_rf_goal10_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal10_dash)



ImpData_missRanger_rf_goal10_dash





ImpData_missRanger_rf_goal10_dash_highest_mse <- ImpData_missRanger_rf_goal10_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal10_dash_highest_mse <- ImpData_missRanger_rf_goal10_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal10_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```

Goal 11

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_11_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_11_dash)
```


```{r}
missRanger_rf_goal11_dash<- randomForest(goal_11_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal11_dash
```


```{r}
ImpData_missRanger_rf_goal11_dash <- as.data.frame(importance(missRanger_rf_goal11_dash))
ImpData_missRanger_rf_goal11_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal11_dash)



ImpData_missRanger_rf_goal11_dash





ImpData_missRanger_rf_goal11_dash_highest_mse <- ImpData_missRanger_rf_goal11_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal11_dash_highest_mse <- ImpData_missRanger_rf_goal11_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal11_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Goal 12 

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_12_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_12_dash)
```


```{r}
missRanger_rf_goal12_dash<- randomForest(goal_12_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal12_dash
```


```{r}
ImpData_missRanger_rf_goal12_dash <- as.data.frame(importance(missRanger_rf_goal12_dash))
ImpData_missRanger_rf_goal12_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal12_dash)



ImpData_missRanger_rf_goal12_dash





ImpData_missRanger_rf_goal12_dash_highest_mse <- ImpData_missRanger_rf_goal12_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal12_dash_highest_mse <- ImpData_missRanger_rf_goal12_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal12_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 13

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_13_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_13_dash)
```


```{r}
missRanger_rf_goal13_dash<- randomForest(goal_13_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal13_dash
```


```{r}
ImpData_missRanger_rf_goal13_dash <- as.data.frame(importance(missRanger_rf_goal13_dash))
ImpData_missRanger_rf_goal13_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal13_dash)



ImpData_missRanger_rf_goal13_dash





ImpData_missRanger_rf_goal13_dash_highest_mse <- ImpData_missRanger_rf_goal13_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal13_dash_highest_mse <- ImpData_missRanger_rf_goal13_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal13_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```





Goal 14

```{r}
dash_data_sids_missRanger_sdg_indicators$goal_14_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_14_dash)
```


```{r}
missRanger_rf_goal14_dash<- randomForest(goal_14_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal14_dash
```


```{r}
ImpData_missRanger_rf_goal14_dash <- as.data.frame(importance(missRanger_rf_goal14_dash))
ImpData_missRanger_rf_goal14_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal14_dash)



ImpData_missRanger_rf_goal14_dash





ImpData_missRanger_rf_goal14_dash_highest_mse <- ImpData_missRanger_rf_goal14_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 114)


```

```{r}
ImpData_missRanger_rf_goal14_dash_highest_mse <- ImpData_missRanger_rf_goal14_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal14_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 15


```{r}
dash_data_sids_missRanger_sdg_indicators$goal_15_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_15_dash)
```


```{r}
missRanger_rf_goal15_dash<- randomForest(goal_15_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal15_dash
```


```{r}
ImpData_missRanger_rf_goal15_dash <- as.data.frame(importance(missRanger_rf_goal15_dash))
ImpData_missRanger_rf_goal15_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal15_dash)



ImpData_missRanger_rf_goal15_dash





ImpData_missRanger_rf_goal15_dash_highest_mse <- ImpData_missRanger_rf_goal15_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal15_dash_highest_mse <- ImpData_missRanger_rf_goal15_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal15_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```





Goal 16


```{r}
dash_data_sids_missRanger_sdg_indicators$goal_16_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_16_dash)
```


```{r}
missRanger_rf_goal16_dash<- randomForest(goal_16_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal16_dash
```


```{r}
ImpData_missRanger_rf_goal16_dash <- as.data.frame(importance(missRanger_rf_goal16_dash))
ImpData_missRanger_rf_goal16_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal16_dash)



ImpData_missRanger_rf_goal16_dash





ImpData_missRanger_rf_goal16_dash_highest_mse <- ImpData_missRanger_rf_goal16_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 116)


```

```{r}
ImpData_missRanger_rf_goal16_dash_highest_mse <- ImpData_missRanger_rf_goal16_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal16_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 17


```{r}
dash_data_sids_missRanger_sdg_indicators$goal_17_dash <- as.factor(dash_data_sids_missRanger_sdg_indicators$goal_17_dash)
```


```{r}
missRanger_rf_goal17_dash<- randomForest(goal_17_dash ~ ., data = dash_data_sids_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal17_dash
```


```{r}
ImpData_missRanger_rf_goal17_dash <- as.data.frame(importance(missRanger_rf_goal17_dash))
ImpData_missRanger_rf_goal17_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal17_dash)



ImpData_missRanger_rf_goal17_dash





ImpData_missRanger_rf_goal17_dash_highest_mse <- ImpData_missRanger_rf_goal17_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal17_dash_highest_mse <- ImpData_missRanger_rf_goal17_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal17_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Investigating


```{r}
s <- ggplot(dash_data_sids_missRanger_sdg_indicators, aes(x = 	
parties_meeting_their_commitments_and_obligations_in_transmitting_information_as_required_by_rotterdam_convention_on_hazardous_waste_and_other_chemicals,
                                                y = rownames(dash_data_sids_missRanger_sdg_indicators), label = row.names(dash_data_sids_missRanger_sdg_indicators))) +
  geom_point()

ggplotly(s)
```

