---
title: "clustImpute_most_recent"
author: "Connor Flynn"
date: "7/25/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

Goal: There are 4 goals of this Rmd
  1. Impute missing data using the ClustImpute() method
  2. Cluster the newly imputed data using kmeans, and visualize clusters
  3. Plot example indicators to compare "true" vs imputed data
  4. Determine variable importance by using Random Forest Regression
    ex. What are the most important indicators in predicting y indicator
  
  
Decision Making:
  1. How much data do we impute
    - All of it?
    - Only indicators in which x percentage of SIDS have data 
  2. How many clusters do we put into the ClustImpute function
  3. How many clusters do we put into the kmeans() function (assisted by elbow plot from fviz_nrcluster)

## Load Libraries

The code chunk below reads in packages and functions used in this workflow:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                dplyr,
                missRanger,
                cluster,
                factoextra,
                randomForest,
                ClustImpute)




options(scipen = 99)
options(ggrepel.max.overlaps = Inf)
set.seed(3)
```

Import data
```{r}
sdg_indicators <- read_csv(here("most_recent/data_cleaned_and_summarized/sdg_indicators_joined_most_recent.csv"))
```


Drop Cuba and Singapore from the data because they are both significant outliers.
Drop SIDS and Bonaire Sint Eustatius and Saba because they only appear in a few goals
```{r}
sdg_indicators<- sdg_indicators %>% 
  filter(geo_area_name != "Cuba",
         geo_area_name != "Singapore",
         geo_area_name != "Small_island_developing_States_(SIDS)",
         geo_area_name != "Bonaire,_Sint_Eustatius_and_Saba")
         #  geo_area_name != "Jamaica",
         #  geo_area_name != "Puerto_Rico",
         # geo_area_name != "Haiti",
         # geo_area_name != "Dominican_Republic")
```


Convert the first column (country names) to row names
```{r}
sdg_indicators <- sdg_indicators %>% 
  remove_rownames %>% 
  column_to_rownames(var="geo_area_name")
```



*Determine how much data we want to impute
  - Here, I decided that I only want to include columns (indicators) in which at least 40% of the SIDS have data for
```{r}
sdg_indicators_less_na <- sdg_indicators[, which(colMeans(!is.na(sdg_indicators)) > 0.4)]
```



Impute using ClustImpute

* For nr_cluster = x, we are determining the number of clusters that we believe there are in the data
  - This number can be changed and has significant influence on the output data

```{r}
res <- ClustImpute(sdg_indicators_less_na, nr_cluster = 7)
```



Go into the ClustImpute object and retrieve the imputed data frame

```{r}

sdg_indicators_ClustImpute <- res$complete_data

```



Remove columns with 0 variance because columns with 0 variance cause an error in clustering

```{r}
sdg_indicators_ClustImpute_variance <- sdg_indicators_ClustImpute[, sapply(sdg_indicators_ClustImpute, var) != 0]
```


This visualization helps us to determine the number of clusters that should be used in the kmeans() function

```{r}
fviz_nbclust(sdg_indicators_ClustImpute_variance, kmeans, method = "wss")
```


Cluster the newly imputed data
```{r}
set.seed(3)
kmeans2 <- kmeans(sdg_indicators_ClustImpute_variance, center = 5, nstart = 100)
```

Visualize clusters
```{r}
fviz_cluster(kmeans2, data = sdg_indicators_ClustImpute_variance,
geom = c("text","point"),
             repel = TRUE,            # Avoid label overlapping
             show.clust.cent = TRUE, # Show cluster centers
             palette = "lancet",         # Color palette see ?ggpubr::ggpar
             ggtheme = theme_bw()+
              theme(axis.text.x = element_text( hjust = 0.5, vjust = 0.5, size=15),
        axis.title.x =element_text(size=20),
        axis.text.y = element_text(hjust = 0.5, vjust = 0.5, size=15),
        axis.title.y =element_text(size=20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.text = element_text(size=25)))
```




True vs Imputed Data Comparisons

Goal 1

```{r}
goal1_na_example <- row.names(sdg_indicators)[which(is.na(sdg_indicators$proportion_of_population_below_international_poverty_line_percent))]

cat(paste(goal1_na_example),sep=",")
```



```{r}
ggplot(data = sdg_indicators_ClustImpute_variance, aes(y = rownames(sdg_indicators_ClustImpute_variance), 
                                            x =  proportion_of_population_below_international_poverty_line_percent,
                                            fill = rownames(sdg_indicators_ClustImpute_variance))) +
  geom_col(show.legend = FALSE) + 
  scale_fill_manual(values = c(Anguilla = "blue",  
                               Belize = "blue",
                               Cook_Islands = "blue",       
                               Palau = "blue",
                               Puerto_Rico = "blue",   
                               Suriname = "blue",
                               Trinidad_and_Tobago = "blue",
                               United_States_Virgin_Islands = "blue",
                               Aruba = "blue",
                               Bahamas = "blue",
                               Barbados = "blue",
                               British_Virgin_Islands = "blue",
                               Dominica = "blue", 
                               Grenada = "blue", 
                               Guyana = "blue",
                               Saint_Vincent_and_the_Grenadines = "blue",
                               Antigua_and_Barbuda = "blue",
                               Saint_Kitts_and_Nevis = "blue",              
                               Curaçao = "blue",
                               New_Caledonia = "blue",
                               "Sint_Maarten_(Dutch_part)" = "blue",           
                               American_Samoa = "blue",
                               French_Polynesia = "blue",            
                               Guam = "blue",
                               Niue         = "blue",
                               Northern_Mariana_Islands = "blue",              
                               Montserrat = "blue"))
```


Goal 13

```{r}
goal13_na_example <- row.names(sdg_indicators)[which(is.na(sdg_indicators$number_of_directly_affected_persons_attributed_to_disasters_per_100_000_population_number))]

cat(paste(goal13_na_example),sep=",")

```



```{r}
ggplot(data = sdg_indicators_ClustImpute_variance, aes(y = rownames(sdg_indicators_ClustImpute_variance), 
                                            x =  number_of_directly_affected_persons_attributed_to_disasters_per_100_000_population_number,
                                            fill = rownames(sdg_indicators_ClustImpute_variance))) +
  geom_col(show.legend = FALSE)  +
  scale_fill_manual(values = c(Anguilla = "blue",
                               Dominican_Republic = "blue",
                               Haiti = "blue",
                               Puerto_Rico = "blue",
                               Suriname = "blue",
                               United_States_Virgin_Islands = "blue",
                               Aruba = "blue",
                               Bahamas = "blue",
                               British_Virgin_Islands = "blue",
                               Sao_Tome_and_Principe = "blue",
                               Curaçao = "blue",
                               Nauru = "blue",
                               'Sint_Maarten_(Dutch_part)' = "blue",
                               Montserrat = "blue"))




```

Goal 3

```{r}
goal3_na_example <- row.names(sdg_indicators)[which(is.na(sdg_indicators$crude_death_rate_attributed_to_household_and_ambient_air_pollution_deaths_per_100_000_population))]

cat(paste(goal3_na_example),sep=",")

```

```{r}
ggplot(data = sdg_indicators_ClustImpute_variance, aes(y = rownames(sdg_indicators_ClustImpute_variance), 
                                            x =  crude_death_rate_attributed_to_household_and_ambient_air_pollution_deaths_per_100_000_population,
                                            fill = rownames(sdg_indicators_ClustImpute_variance))) +
  geom_col(show.legend = FALSE)  +
  scale_fill_manual(values = c(Anguilla = "blue",
                               Cook_Islands = "blue",
                               Palau = "blue",
                               Puerto_Rico = "blue",
                               United_States_Virgin_Islands = "blue",
                               Aruba = "blue",
                               British_Virgin_Islands = "blue",
                               Dominica = "blue",
                               Saint_Kitts_and_Nevis = "blue",
                               Curaçao = "blue",
                               Marshall_Islands = "blue",
                               Nauru = "blue",
                               Tuvalu = "blue",
                               New_Caledonia = "blue",
                               "Sint_Maarten_(Dutch_part)" = "blue",
                               American_Samoa = "blue",
                               French_Polynesia = "blue",
                               Guam = "blue",
                               Niue = "blue",
                               Northern_Mariana_Islands = "blue",
                               Montserrat = "blue"))
```



Goal 4 

```{r}
goal4_na_example <- row.names(sdg_indicators)[which(is.na(sdg_indicators$proportion_of_schools_with_access_to_computers_for_pedagogical_purposes_by_education_level_percent))]

cat(paste(goal4_na_example),sep=",")
```


```{r}
ggplot(data = sdg_indicators_ClustImpute_variance, aes(y = rownames(sdg_indicators_ClustImpute_variance), 
                                            x =  proportion_of_schools_with_access_to_computers_for_pedagogical_purposes_by_education_level_percent,
                                            fill = rownames(sdg_indicators_ClustImpute_variance))) +
  geom_col(show.legend = FALSE)  +
  scale_fill_manual(values = c(Belize = "blue",
                               Dominican_Republic = "blue",
                               Fiji = "blue",
                               Haiti = "blue",
                               'Micronesia_(Federated_States_of)' = "blue",
                               Puerto_Rico = "blue",
                               Suriname = "blue",
                               'Timor-Leste' = "blue",
                               Trinidad_and_Tobago = "blue",
                               United_States_Virgin_Islands = "blue",
                               Vanuatu = "blue",
                               Bahamas = "blue",
                               Barbados = "blue",
                               Guyana = "blue",
                               Papua_New_Guinea = "blue",
                               Curaçao = "blue",
                              'Guinea-Bissau' = "blue",
                               New_Caledonia = "blue",
                               American_Samoa = "blue",
                               French_Polynesia = "blue",
                               Guam = "blue",
                               Northern_Mariana_Islands = "blue"))
```


Goal 7

```{r}
goal7_na_example <- row.names(sdg_indicators)[which(is.na(sdg_indicators$proportion_of_population_with_access_to_electricity_by_urban_rural_percent))]

cat(paste(goal7_na_example),sep=",")
```



```{r}
ggplot(data = sdg_indicators_ClustImpute_variance, aes(y = rownames(sdg_indicators_ClustImpute_variance), 
                                            x =  proportion_of_population_with_access_to_electricity_by_urban_rural_percent,
                                            fill = rownames(sdg_indicators_ClustImpute_variance))) +
  geom_col(show.legend = FALSE)  +
  scale_fill_manual(values = c(American_Samoa = "blue",
                               Montserrat = "blue"))
```









```{r}
# ggplot() + 
#   geom_point(data = sdg_indicators_ClustImpute, aes(y = rownames(sdg_indicators_ClustImpute),
#                                         x = proportion_of_population_with_access_to_electricity_by_urban_rural_percent),
#              color = "black") + 
#   theme_minimal()
# 
# ggplot() +
#   geom_point(data = sdg_indicators, aes(y = rownames(sdg_indicators),
#                                         x = proportion_of_population_with_access_to_electricity_by_urban_rural_percent),
#              color = "black") +
#   theme_minimal()
```


Random Forest

Here, we use a random forest to determine variable importance in predicting indicators


Create random forest object from imputed data
```{r}
ClustImpute_rf <- randomForest(proportion_of_population_below_international_poverty_line_percent ~ ., data = sdg_indicators_ClustImpute_variance, 
                   importance = TRUE)
```


View summary of random forest
  - Ideally, we want high variance explained and a low mean of squared residuals
```{r}
ClustImpute_rf
```


View variable importance measured in both % increase in mean squared error (preferred) and inc node impurity
```{r}
ImpData <- as.data.frame(importance(ClustImpute_rf))
ImpData$Var.Names <- row.names(ImpData)

# ggplot(ImpData, aes(x=Var.Names, y=`%IncMSE`)) +
#   geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`%IncMSE`), color="skyblue") +
#   geom_point(aes(size = IncNodePurity), color="blue", alpha=0.6) +
#   theme_light() +
#   coord_flip() +
#   theme(
#     legend.position="bottom",
#     panel.grid.major.y = element_blank(),
#     panel.border = element_blank(),
#     axis.ticks.y = element_blank()
#   )

View(ImpData)
```

