---
title: "aggregated_sdg_status"
author: "Connor Flynn"
date: "8/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(dplyr)
library(missRanger)
library(randomForest)
library(edarf)
library(janitor)
library(caret)
library(randomForestExplainer)

options(set.seed(3))
```

```{r}
set.seed(3)
```




Step 1: Read in data that is summarized by taking the most recent year of data for each indicator/SIDS. If there are multiple indicator values for the most recent year/SIDS, the mean of those values is taken.

```{r}
sdg_indicators <- read_csv(here("most_recent/data_cleaned_and_summarized/sdg_indicators_joined_most_recent.csv"))
```


Step 2: Impute this data using random forest imputation with the missRanger package

Determine how much data we want to impute
  - Here, I decided that I only want to include columns (indicators) in which at least 40% of the SIDS have data for
```{r}
sdg_indicators_less_na <- sdg_indicators[, which(colMeans(!is.na(sdg_indicators)) > 0.4)]
```


Impute using missRanger function (Random Forest Imputation)
```{r, message=FALSE}
sdg_indicators_missRanger <- missRanger(sdg_indicators_less_na, 
                                        formula = . ~ ., 
                                        num.trees = 1000,
                                        seed = 3,
                                        returnOOB = TRUE
                                      )
```



Step 3: Read in data from the Sustainable Development Report 2022 for the most recent goal classification(color) for each SIDS/SDG


```{r}
sdg_report_classifier_data <- read_csv(here("data/sdg_data/sustainable_development_report_2022.csv"))
```



Clean, Select Classifier Data

```{r}
sdg_report_classifier_data <- clean_names(sdg_report_classifier_data)
```

```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>%
     mutate(country = recode(country, 
                            "Bahamas, The" = 'Bahamas',
                             "Micronesia, Fed. Sts." = 	"Micronesia_(Federated_States_of)",
                            "St. Kitts and Nevis" = 	"Saint_Kitts_and_Nevis",
                            	"St. Lucia" = 	"Saint_Lucia", 
                            	"St. Vincent and the Grenadines" = "Saint_Vincent_and_the_Grenadines"
                            
                            ))
```



```{r}
sdg_report_classifier_data$country <- gsub(" ", "_", sdg_report_classifier_data$country)
```

```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>%
  rename(geo_area_name = country)
```


```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```



Left join to match Sustainable Development Report SIDS(37) with all SIDS(54)
```{r}
sdg_report_classifier_data <- left_join(sdg_indicators, sdg_report_classifier_data, by = "geo_area_name")
```




```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```

Drop SIDS that were not a part of the 2022 Sustainable Development Report
```{r}
sdg_report_classifier_data <- drop_na(sdg_report_classifier_data)
```


```{r}
sdg_report_classifier_data_matrix <- sdg_report_classifier_data %>% 
  select(-geo_area_name)
  
```


```{r}
sdg_report_classifier_data_matrix[sdg_report_classifier_data_matrix == "yellow"] <- "green"

sdg_report_classifier_data_matrix[sdg_report_classifier_data_matrix == "orange"] <- "green"

sdg_report_classifier_data_matrix[sdg_report_classifier_data_matrix == "grey"] <- "red"
```

```{r}
# model.matrix(~0+., data=sdg_report_classifier_data_matrix) %>% 
#   cor(use="pairwise.complete.obs") %>% 
#   ggcorrplot(show.diag = F, type = "lower", lab=TRUE, lab_size=1, 
# tl.cex = 7)
```


Step 4: Join Step 1 Data with Step 3 Data

Join SIDS classification data with tier 1 and tier 2 indicator data for 37 SIDS
```{r}
sdg_report_classifier_data_missRanger_sdg_indicators <- left_join(sdg_report_classifier_data, sdg_indicators_missRanger, by = "geo_area_name")
```


Join Isolation Data
```{r}
isolation <- read_csv(here("data/sdg_data/isolation_evi.csv"))
```

```{r}
isolation <- isolation %>%
  rename(geo_area_name = Country_EVI)
```


```{r}
isolation$geo_area_name <- gsub(" ", "_", isolation$geo_area_name)
```


```{r}
isolation <- isolation %>%
     mutate(geo_area_name = recode(geo_area_name, 
                            "Bahama" = 'Bahamas',
                             "Fed._States_Micronesia" = 	"Micronesia_(Federated_States_of)",
                            "St._Kitts_and_Nevis" = 	"Saint_Kitts_and_Nevis",
                            	"St._Vincent_&_Grenadines" = "Saint_Vincent_and_the_Grenadines",
                            "Antigua_&_Barbuda" = "Antigua_and_Barbuda",
                            "Sao_Tome_&_Principe" =  "Sao_Tome_and_Principe",
                            "Cape_Verde" = "Cabo_Verde",
                            "Dominican_Rep" = "Dominican_Republic"
                            
                            ))
```




```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- left_join(sdg_report_classifier_data_missRanger_sdg_indicators, isolation, by = "geo_area_name")

sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>% 
  select(geo_area_name, ISOL)

# Timor Leste - 575
# Dominica - 568

sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>%                               # Replacing values
  mutate(ISOL = replace(ISOL, geo_area_name == "Dominica", 568))

sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>%                               # Replacing values
  mutate(ISOL = replace(ISOL, geo_area_name == "Timor-Leste", 575))

```


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>% 
  remove_rownames %>% 
  column_to_rownames(var="geo_area_name")
```



Aggregate SDG Status (Color)

Green = Green/Yellow/Orange
Red = Red/Grey



```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation[sdg_report_classifier_data_missRanger_sdg_indicators_isolation == "yellow"] <- "green"
```

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation[sdg_report_classifier_data_missRanger_sdg_indicators_isolation == "orange"] <- "red"
```

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation[sdg_report_classifier_data_missRanger_sdg_indicators_isolation == "grey"] <- "red"
```












Step 5: Run Random Forest Classification Models predicting the color(classification) of each SDG for each SIDS

What are the drivers/most important predictors of the status(color) of a SIDS two lowest performing indicators per SDG?

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_1_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_1_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_2_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_2_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_3_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_3_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_4_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_4_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_5_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_5_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_6_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_6_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_7_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_7_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_8_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_8_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_9_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_9_dash)


sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_10_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_10_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_11_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_11_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_12_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_12_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_13_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_13_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_14_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_14_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_15_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_15_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_16_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_16_dash)

sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_17_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators_isolation$goal_17_dash)


```

Goal 4 

Indicators
- Participation rate in pre-primary organized learning (% of children aged 4 to 6)
- Net primary enrollment rate (%)
- Lower secondary completion rate (%)
- Literacy rate (% of population aged 15 to 24)
- Tertiary educational attainment (% of population aged 25 to 34)
- PISA score (worst 0-600 best)
- Variation in science performance explained by socio-economic status (%)
- Underachievers in science (% of 15-year-olds) 




```{r}
missRanger_rf_goal4_dash<- randomForest(goal_4_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators_isolation, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal4_dash
```


```{r}
#randomForestExplainer::explain_forest(missRanger_rf_goal4_dash, interactions = TRUE)
```

```{r}
#randomForestExplainer::plot_predict_interaction()
```


```{r}
randomForestExplainer::plot_predict_interaction(forest = missRanger_rf_goal4_dash, 
                                                data = sdg_report_classifier_data_missRanger_sdg_indicators_isolation,
                                                variable1 = "ilo_proportion_of_mothers_with_newborns_receiving_maternity_cash_benefit_percent",
                                                variable2 = "participation_rate_in_organized_learning_one_year_before_the_official_primary_entry_age_by_sex_percent")
```

```{r}
ggplot(sdg_indicators, aes(x = completion_rate_by_sex_location_wealth_quintile_and_education_level_percent, y = geo_area_name)) +
  geom_point()
```

```{r}
missRanger_rf_goal4_dash<- randomForest(completion_rate_by_sex_location_wealth_quintile_and_education_level_percent ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators_isolation, 
                   importance = TRUE)
```

```{r}
missRanger_rf_goal4_dash
```

```{r}
ImpData <- as.data.frame(importance(missRanger_rf_goal4_dash))
ImpData$Var.Names <- row.names(ImpData)

# ggplot(ImpData, aes(x=Var.Names, y=`%IncMSE`)) +
#   geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`%IncMSE`), color="skyblue") +
#   geom_point(aes(size = IncNodePurity), color="blue", alpha=0.6) +
#   theme_light() +
#   coord_flip() +
#   theme(
#     legend.position="bottom",
#     panel.grid.major.y = element_blank(),
#     panel.border = element_blank(),
#     axis.ticks.y = element_blank()
#   )
```


```{r}
randomForestExplainer::plot_predict_interaction(forest = missRanger_rf_goal4_dash, 
                                                data = sdg_report_classifier_data_missRanger_sdg_indicators_isolation,
                                                variable1 = "mortality_rate_attributed_to_unsafe_water_unsafe_sanitation_and_lack_of_hygiene_deaths_per_100_000_population",
                                                variable2 = "employed_population_below_international_poverty_line_by_sex_and_age_percent") +
  labs(title = "Prediction Interaction: Percent Completion of Primary and Secondary Education",
       x = "Mortality Rate Attributed to Unsafe Drinking Water/Sanitation and Lack of Hygiene (per 100,000 Pop) ",
       y = "Employed Population Below the International Poverty Line (%)",
       fill = "Prediction of Percent Completion (%)") +
  theme(plot.title = element_text(hjust = 0.5))

```


Yale Indicators

```{r}
missRanger_rf_goal3_smr<- randomForest(suicide_mortality_rate_by_sex_deaths_per_100_000_population ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators_isolation, 
                   importance = TRUE)
```


```{r}
ImpData_smr <- as.data.frame(importance(missRanger_rf_goal3_smr))
ImpData_smr$Var.Names <- row.names(ImpData_smr)

# ggplot(ImpData, aes(x=Var.Names, y=`%IncMSE`)) +
#   geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`%IncMSE`), color="skyblue") +
#   geom_point(aes(size = IncNodePurity), color="blue", alpha=0.6) +
#   theme_light() +
#   coord_flip() +
#   theme(
#     legend.position="bottom",
#     panel.grid.major.y = element_blank(),
#     panel.border = element_blank(),
#     axis.ticks.y = element_blank()
#   )
```

```{r}
df_rf_smr<- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>% 
  mutate(predicted = predict(missRanger_rf_goal3_smr))
```



```{r}
imp_df_smr <- data.frame(importance(missRanger_rf_goal3_smr, scale = FALSE, type = 1))
# Tidy up and sort the data frame
imp_df_smr <- imp_df_smr %>% 
  mutate(names = rownames(imp_df_smr)) %>% 
  arrange(desc(X.IncMSE))
# Plot mean decreased accuracy
imp_df_smr %>% 
  top_n(10, X.IncMSE) %>% 
  ggplot(aes(x = reorder(names, X.IncMSE),y = X.IncMSE)) +
  geom_col() +
  coord_flip() +
  labs(title = "Variable Importance",
       subtitle = "Random Forests (N = 500)",
       x= "",
       y= "Mean Decrease in Accuracy") +
  theme(plot.caption = element_text(face = "italic"))

```



```{r}
# Save top predictor names as character vector
nm_smr <- as.character(imp_df_smr$names)[1:12]
# Get partial depedence values for top predictors
pd_df_smr <- partial_dependence(fit = missRanger_rf_goal3_smr,
                         vars = nm_smr,
                         data = df_rf_smr)
                         # n = c(100, 500))
```


```{r}
# Plot partial dependence using edarf
plot_pd(pd_df_smr)
```
```{r}
randomForestExplainer::plot_predict_interaction(forest = missRanger_rf_goal3_smr, 
                                                data = sdg_report_classifier_data_missRanger_sdg_indicators_isolation,
                                                variable1 = "number_of_disruptions_to_educational_services_attributed_to_disasters_number",
                                                variable2 = "forest_area_as_a_proportion_of_total_land_area_percent")
```

```{r}
ggplot(sdg_report_classifier_data_missRanger_sdg_indicators_isolation, aes( x = mortality_rate_attributed_to_cardiovascular_disease_cancer_diabetes_or_chronic_respiratory_disease_probability,
                                                                            y = suicide_mortality_rate_by_sex_deaths_per_100_000_population)) +
  geom_point(method = lm)
```

