---
title: "random_forest_SDR_2022"
author: "Connor Flynn"
date: "8/4/2022"
output: html_document
---

Rmd Outline

Goal: Using both Tier 1 and Tier 2 SDG Indicators, Explore the question ->  What are the drivers/most important predictors of the status(color) of a SIDS two lowest performing indicators per SDG? 

Useful Links:
Data Souces
https://dashboards.sdgindex.org/downloads
https://unstats.un.org/sdgs/dataportal/database

Metadata
https://unstats.un.org/sdgs/files/Tier%20Classification%20of%20SDG%20Indicators_9%20Jun%202022_web.pdf
https://unstats.un.org/sdgs/metadata/

Methodology
https://dashboards.sdgindex.org/downloads

Step 1: Read in data that is summarized by taking the most recent year of data for each indicator/SIDS. If there are multiple indicator values for the most recent year/SIDS, the mean of those values is taken.
  - The data is cleaned and summarized in the rmd's contained in this folder SIDS_SDG_UNSTATS/most_recent/data_cleaned_and_summarized
  - The data is joined in the combine_most_recent_data.Rmd
  
Step 2: Impute this data using random forest imputation with the missRanger package

Step 3: Read in data from the Sustainable Development Report 2022 for the most recent goal dashes(colors)
  - green: Goal Achievement 
  - yellow: Challenges Remain
  - orange: Significant Challenges
  - red: Major Challenges
  - grey: Insufficient Data
  

Each Tier 1 SDG Indicator is assigned a color based on thresholds of the indicator value

Each Tier SDG is is assigned a color based on the colors of it's indicators
 - "We then took the average of the two rescaled variables on which the country performed worst to identify the rating
for the goal. We applied the added rule that in order to score green for the goal both indicators had to be green –
otherwise the goal would be rated yellow. Similarly, a red score was applied only if both worst-performing
indicators score red. If the country has only one data point under the SDG then the color rating for that indicator
determines the overall rating for the goal. If the country has less than 50% of the indicators available under a goal
the dashboard color for that goal is “grey”."

Step 4: Join Step 1 Data with Step 3 Data


Step 5: Run Random Forest Classification Models predicting the color(classification) of each SDG for each SIDS

Step 6: Determine Variable Importance from each random forest model




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                dplyr,
                missRanger,
                cluster,
                factoextra,
                randomForest,
                plotly,
                kableExtra,
                randomForestExplainer)



options(set.seed(3))
options(scipen = 99)
```


Step 1: Read in data that is summarized by taking the most recent year of data for each indicator/SIDS. If there are multiple indicator values for the most recent year/SIDS, the mean of those values is taken.

```{r}
sdg_indicators <- read_csv(here("most_recent/data_cleaned_and_summarized/sdg_indicators_joined_most_recent.csv"))
```


Step 2: Impute this data using random forest imputation with the missRanger package

Determine how much data we want to impute
  - Here, I decided that I only want to include columns (indicators) in which at least 40% of the SIDS have data for
```{r}
sdg_indicators_less_na <- sdg_indicators[, which(colMeans(!is.na(sdg_indicators)) > 0.4)]
```


Impute using missRanger function (Random Forest Imputation)
```{r}
sdg_indicators_missRanger <- missRanger(sdg_indicators_less_na, 
                                        formula = . ~ ., 
                                        num.trees = 1000,
                                        seed = 3,
                                        returnOOB = TRUE
                                      )
```



Step 3: Read in data from the Sustainable Development Report 2022 for the most recent goal classification(color) for each SIDS/SDG


```{r}
sdg_report_classifier_data <- read_csv(here("data/sdg_data/sustainable_development_report_2022.csv"))
```



Clean, Select Classifier Data

```{r}
sdg_report_classifier_data <- clean_names(sdg_report_classifier_data)
```

```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>%
     mutate(country = recode(country, 
                            "Bahamas, The" = 'Bahamas',
                             "Micronesia, Fed. Sts." = 	"Micronesia_(Federated_States_of)",
                            "St. Kitts and Nevis" = 	"Saint_Kitts_and_Nevis",
                            	"St. Lucia" = 	"Saint_Lucia", 
                            	"St. Vincent and the Grenadines" = "Saint_Vincent_and_the_Grenadines"
                            
                            ))
```



```{r}
sdg_report_classifier_data$country <- gsub(" ", "_", sdg_report_classifier_data$country)
```

```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>%
  rename(geo_area_name = country)
```


```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```



Left join to match Sustainable Development Report SIDS(37) with all SIDS(54)
```{r}
sdg_report_classifier_data <- left_join(sdg_indicators, sdg_report_classifier_data, by = "geo_area_name")
```




```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```

Drop SIDS that were not a part of the 2022 Sustainable Development Report
```{r}
sdg_report_classifier_data <- drop_na(sdg_report_classifier_data)
```



Step 4: Join Step 1 Data with Step 3 Data

Join SIDS classification data with tier 1 and tier 2 indicator data for 37 SIDS
```{r}
sdg_report_classifier_data_missRanger_sdg_indicators <- left_join(sdg_report_classifier_data, sdg_indicators_missRanger, by = "geo_area_name")
```

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators <- sdg_report_classifier_data_missRanger_sdg_indicators %>% 
  remove_rownames %>% 
  column_to_rownames(var="geo_area_name")
```


Step 5: Run Random Forest Classification Models predicting the color(classification) of each SDG for each SIDS

What are the drivers/most important predictors of the status(color) of a SIDS two lowest performing indicators per SDG?


Goal 1

Drop Cuba and Singapore to test model accuracy

# ```{r}
# sdg_report_classifier_data_missRanger_sdg_indicators_cuba_singapore <- sdg_report_classifier_data_missRanger_sdg_indicators %>% 
#   filter(geo_area_name != "Cuba",
#          geo_area_name != "Singapore")
# ```


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_1_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_1_dash)
```


```{r}
missRanger_rf_goal1_dash<- randomForest(goal_1_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal1_dash
```


```{r}
ImpData_missRanger_rf_goal1_dash <- as.data.frame(importance(missRanger_rf_goal1_dash))
ImpData_missRanger_rf_goal1_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal1_dash)



ImpData_missRanger_rf_goal1_dash





ImpData_missRanger_rf_goal1_dash_highest_mse <- ImpData_missRanger_rf_goal1_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal1_dash_highest_mse <- ImpData_missRanger_rf_goal1_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal1_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 2 

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_2_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_2_dash)
```


```{r}
missRanger_rf_goal2_dash<- randomForest(goal_2_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal2_dash
```


```{r}
ImpData_missRanger_rf_goal2_dash <- as.data.frame(importance(missRanger_rf_goal2_dash))
ImpData_missRanger_rf_goal2_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal2_dash)



ImpData_missRanger_rf_goal2_dash





ImpData_missRanger_rf_goal2_dash_highest_mse <- ImpData_missRanger_rf_goal2_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal2_dash_highest_mse <- ImpData_missRanger_rf_goal2_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal2_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```


Goal 3

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_3_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_3_dash)
```


```{r}
missRanger_rf_goal3_dash<- randomForest(goal_3_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal3_dash
```


```{r}
ImpData_missRanger_rf_goal3_dash <- as.data.frame(importance(missRanger_rf_goal3_dash))
ImpData_missRanger_rf_goal3_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal3_dash)



ImpData_missRanger_rf_goal3_dash





ImpData_missRanger_rf_goal3_dash_highest_mse <- ImpData_missRanger_rf_goal3_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal3_dash_highest_mse <- ImpData_missRanger_rf_goal3_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal3_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 4 

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_4_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_4_dash)
```


```{r}
missRanger_rf_goal4_dash<- randomForest(goal_4_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal4_dash
```


```{r}
ImpData_missRanger_rf_goal4_dash <- as.data.frame(importance(missRanger_rf_goal4_dash))
ImpData_missRanger_rf_goal4_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal4_dash)



ImpData_missRanger_rf_goal4_dash





ImpData_missRanger_rf_goal4_dash_highest_mse <- ImpData_missRanger_rf_goal4_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal4_dash_highest_mse <- ImpData_missRanger_rf_goal4_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal4_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 5 



```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_5_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_5_dash)
```


```{r}
missRanger_rf_goal5_dash<- randomForest(goal_5_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal5_dash
```


```{r}
ImpData_missRanger_rf_goal5_dash <- as.data.frame(importance(missRanger_rf_goal5_dash))
ImpData_missRanger_rf_goal5_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal5_dash)



ImpData_missRanger_rf_goal5_dash





ImpData_missRanger_rf_goal5_dash_highest_mse <- ImpData_missRanger_rf_goal5_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal5_dash_highest_mse <- ImpData_missRanger_rf_goal5_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal5_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```

Goal 6 

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_6_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_6_dash)
```


```{r}
missRanger_rf_goal6_dash<- randomForest(goal_6_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal6_dash
```


```{r}
ImpData_missRanger_rf_goal6_dash <- as.data.frame(importance(missRanger_rf_goal6_dash))
ImpData_missRanger_rf_goal6_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal6_dash)



ImpData_missRanger_rf_goal6_dash





ImpData_missRanger_rf_goal6_dash_highest_mse <- ImpData_missRanger_rf_goal6_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal6_dash_highest_mse <- ImpData_missRanger_rf_goal6_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal6_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.5) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```





Goal 7 

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_7_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_7_dash)
```


```{r}
missRanger_rf_goal7_dash<- randomForest(goal_7_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal7_dash
```


```{r}
ImpData_missRanger_rf_goal7_dash <- as.data.frame(importance(missRanger_rf_goal7_dash))
ImpData_missRanger_rf_goal7_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal7_dash)



ImpData_missRanger_rf_goal7_dash





ImpData_missRanger_rf_goal7_dash_highest_mse <- ImpData_missRanger_rf_goal7_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal7_dash_highest_mse <- ImpData_missRanger_rf_goal7_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal7_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```


Goal 8 


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_8_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_8_dash)
```


```{r}
missRanger_rf_goal8_dash<- randomForest(goal_8_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal8_dash
```


```{r}
ImpData_missRanger_rf_goal8_dash <- as.data.frame(importance(missRanger_rf_goal8_dash))
ImpData_missRanger_rf_goal8_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal8_dash)



ImpData_missRanger_rf_goal8_dash





ImpData_missRanger_rf_goal8_dash_highest_mse <- ImpData_missRanger_rf_goal8_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal8_dash_highest_mse <- ImpData_missRanger_rf_goal8_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal8_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 9 


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_9_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_9_dash)
```


```{r}
missRanger_rf_goal9_dash<- randomForest(goal_9_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal9_dash
```


```{r}
ImpData_missRanger_rf_goal9_dash <- as.data.frame(importance(missRanger_rf_goal9_dash))
ImpData_missRanger_rf_goal9_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal9_dash)



ImpData_missRanger_rf_goal9_dash





ImpData_missRanger_rf_goal9_dash_highest_mse <- ImpData_missRanger_rf_goal9_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal9_dash_highest_mse <- ImpData_missRanger_rf_goal9_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal9_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Goal 10 

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_10_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_10_dash)
```


```{r}
missRanger_rf_goal10_dash<- randomForest(goal_10_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal10_dash
```


```{r}
ImpData_missRanger_rf_goal10_dash <- as.data.frame(importance(missRanger_rf_goal10_dash))
ImpData_missRanger_rf_goal10_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal10_dash)



ImpData_missRanger_rf_goal10_dash





ImpData_missRanger_rf_goal10_dash_highest_mse <- ImpData_missRanger_rf_goal10_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal10_dash_highest_mse <- ImpData_missRanger_rf_goal10_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal10_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```

Goal 11

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_11_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_11_dash)
```


```{r}
missRanger_rf_goal11_dash<- randomForest(goal_11_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal11_dash
```


```{r}
ImpData_missRanger_rf_goal11_dash <- as.data.frame(importance(missRanger_rf_goal11_dash))
ImpData_missRanger_rf_goal11_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal11_dash)



ImpData_missRanger_rf_goal11_dash





ImpData_missRanger_rf_goal11_dash_highest_mse <- ImpData_missRanger_rf_goal11_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal11_dash_highest_mse <- ImpData_missRanger_rf_goal11_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal11_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Goal 12 

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_12_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_12_dash)
```


```{r}
missRanger_rf_goal12_dash<- randomForest(goal_12_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal12_dash
```


```{r}
ImpData_missRanger_rf_goal12_dash <- as.data.frame(importance(missRanger_rf_goal12_dash))
ImpData_missRanger_rf_goal12_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal12_dash)



ImpData_missRanger_rf_goal12_dash





ImpData_missRanger_rf_goal12_dash_highest_mse <- ImpData_missRanger_rf_goal12_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal12_dash_highest_mse <- ImpData_missRanger_rf_goal12_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal12_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 13

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_13_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_13_dash)
```


```{r}
missRanger_rf_goal13_dash<- randomForest(goal_13_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal13_dash
```


```{r}
ImpData_missRanger_rf_goal13_dash <- as.data.frame(importance(missRanger_rf_goal13_dash))
ImpData_missRanger_rf_goal13_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal13_dash)



ImpData_missRanger_rf_goal13_dash





ImpData_missRanger_rf_goal13_dash_highest_mse <- ImpData_missRanger_rf_goal13_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal13_dash_highest_mse <- ImpData_missRanger_rf_goal13_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal13_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```





Goal 14

```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_14_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_14_dash)
```


```{r}
missRanger_rf_goal14_dash<- randomForest(goal_14_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal14_dash
```


```{r}
ImpData_missRanger_rf_goal14_dash <- as.data.frame(importance(missRanger_rf_goal14_dash))
ImpData_missRanger_rf_goal14_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal14_dash)



ImpData_missRanger_rf_goal14_dash





ImpData_missRanger_rf_goal14_dash_highest_mse <- ImpData_missRanger_rf_goal14_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 114)


```

```{r}
ImpData_missRanger_rf_goal14_dash_highest_mse <- ImpData_missRanger_rf_goal14_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal14_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 15


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_15_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_15_dash)
```


```{r}
missRanger_rf_goal15_dash<- randomForest(goal_15_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal15_dash
```


```{r}
ImpData_missRanger_rf_goal15_dash <- as.data.frame(importance(missRanger_rf_goal15_dash))
ImpData_missRanger_rf_goal15_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal15_dash)



ImpData_missRanger_rf_goal15_dash





ImpData_missRanger_rf_goal15_dash_highest_mse <- ImpData_missRanger_rf_goal15_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal15_dash_highest_mse <- ImpData_missRanger_rf_goal15_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal15_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```





Goal 16


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_16_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_16_dash)
```


```{r}
missRanger_rf_goal16_dash<- randomForest(goal_16_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal16_dash
```


```{r}
ImpData_missRanger_rf_goal16_dash <- as.data.frame(importance(missRanger_rf_goal16_dash))
ImpData_missRanger_rf_goal16_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal16_dash)



ImpData_missRanger_rf_goal16_dash





ImpData_missRanger_rf_goal16_dash_highest_mse <- ImpData_missRanger_rf_goal16_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 116)


```

```{r}
ImpData_missRanger_rf_goal16_dash_highest_mse <- ImpData_missRanger_rf_goal16_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal16_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```



Goal 17


```{r}
sdg_report_classifier_data_missRanger_sdg_indicators$goal_17_dash <- as.factor(sdg_report_classifier_data_missRanger_sdg_indicators$goal_17_dash)
```


```{r}
missRanger_rf_goal17_dash<- randomForest(goal_17_dash ~ ., data = sdg_report_classifier_data_missRanger_sdg_indicators, 
                   importance = TRUE)
```


```{r}
missRanger_rf_goal17_dash
```


```{r}
ImpData_missRanger_rf_goal17_dash <- as.data.frame(importance(missRanger_rf_goal17_dash))
ImpData_missRanger_rf_goal17_dash$Var.Names <- row.names(ImpData_missRanger_rf_goal17_dash)



ImpData_missRanger_rf_goal17_dash





ImpData_missRanger_rf_goal17_dash_highest_mse <- ImpData_missRanger_rf_goal17_dash %>% 
  slice_max(MeanDecreaseAccuracy, n = 15)


```

```{r}
ImpData_missRanger_rf_goal17_dash_highest_mse <- ImpData_missRanger_rf_goal17_dash_highest_mse %>% mutate(Var.Names = fct_reorder(Var.Names, .[['MeanDecreaseAccuracy']]))
```


```{r}
ggplot(ImpData_missRanger_rf_goal17_dash_highest_mse, aes(x=Var.Names, y=`MeanDecreaseAccuracy`)) +
  geom_segment( aes(x=Var.Names, xend=Var.Names, y=0, yend=`MeanDecreaseAccuracy`), color="skyblue") +
  geom_point(aes(size = MeanDecreaseGini), color="blue", alpha=0.6) +
  theme_light() +
  coord_flip() +
  theme(
    legend.position="bottom",
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank()
  )
```




Investigating


```{r}
s <- ggplot(sdg_report_classifier_data_missRanger_sdg_indicators, aes(x = 	
food_waste_tonnes,
                                                y = rownames(sdg_report_classifier_data_missRanger_sdg_indicators), label = row.names(sdg_report_classifier_data_missRanger_sdg_indicators))) +
  geom_point()

ggplotly(s)
```
