---
title: "sdg_reference"
author: "Connor Flynn"
date: "8/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(dplyr)
library(missRanger)
library(randomForest)
library(edarf)
library(janitor)
library(caret)
library(plot.matrix)

options(set.seed(3))
```

Step 1: Read in data that is summarized by taking the most recent year of data for each indicator/SIDS. If there are multiple indicator values for the most recent year/SIDS, the mean of those values is taken.

```{r}
sdg_indicators <- read_csv(here("most_recent/data_cleaned_and_summarized/sdg_indicators_joined_most_recent.csv"))
```


Step 2: Impute this data using random forest imputation with the missRanger package

Determine how much data we want to impute
  - Here, I decided that I only want to include columns (indicators) in which at least 40% of the SIDS have data for
```{r}
sdg_indicators_less_na <- sdg_indicators[, which(colMeans(!is.na(sdg_indicators)) > 0.4)]
```


Impute using missRanger function (Random Forest Imputation)
```{r}
sdg_indicators_missRanger <- missRanger(sdg_indicators_less_na, 
                                        formula = . ~ ., 
                                        num.trees = 1000,
                                        seed = 3,
                                        returnOOB = TRUE
                                      )
```



Step 3: Read in data from the Sustainable Development Report 2022 for the most recent goal classification(color) for each SIDS/SDG


```{r}
sdg_report_classifier_data <- read_csv(here("data/sdg_data/sustainable_development_report_2022.csv"))
```



Clean, Select Classifier Data

```{r}
sdg_report_classifier_data <- clean_names(sdg_report_classifier_data)
```

```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>%
     mutate(country = recode(country, 
                            "Bahamas, The" = 'Bahamas',
                             "Micronesia, Fed. Sts." = 	"Micronesia_(Federated_States_of)",
                            "St. Kitts and Nevis" = 	"Saint_Kitts_and_Nevis",
                            	"St. Lucia" = 	"Saint_Lucia", 
                            	"St. Vincent and the Grenadines" = "Saint_Vincent_and_the_Grenadines"
                            
                            ))
```



```{r}
sdg_report_classifier_data$country <- gsub(" ", "_", sdg_report_classifier_data$country)
```

```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>%
  rename(geo_area_name = country)
```


```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```



Left join to match Sustainable Development Report SIDS(37) with all SIDS(54)
```{r}
sdg_report_classifier_data <- left_join(sdg_indicators, sdg_report_classifier_data, by = "geo_area_name")
```




```{r}
sdg_report_classifier_data <- sdg_report_classifier_data %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```

Drop SIDS that were not a part of the 2022 Sustainable Development Report
```{r}
sdg_report_classifier_data <- drop_na(sdg_report_classifier_data)
```



Step 4: Join Step 1 Data with Step 3 Data

Join SIDS classification data with tier 1 and tier 2 indicator data for 37 SIDS
```{r}
sdg_report_classifier_data_missRanger_sdg_indicators <- left_join(sdg_report_classifier_data, sdg_indicators_missRanger, by = "geo_area_name")
```


Join Isolation Data
```{r}
isolation <- read_csv(here("data/sdg_data/isolation_evi.csv"))
```

```{r}
isolation <- isolation %>%
  rename(geo_area_name = Country_EVI)
```


```{r}
isolation$geo_area_name <- gsub(" ", "_", isolation$geo_area_name)
```


```{r}
isolation <- isolation %>%
     mutate(geo_area_name = recode(geo_area_name, 
                            "Bahama" = 'Bahamas',
                             "Fed._States_Micronesia" = 	"Micronesia_(Federated_States_of)",
                            "St._Kitts_and_Nevis" = 	"Saint_Kitts_and_Nevis",
                            	"St._Vincent_&_Grenadines" = "Saint_Vincent_and_the_Grenadines",
                            "Antigua_&_Barbuda" = "Antigua_and_Barbuda",
                            "Sao_Tome_&_Principe" =  "Sao_Tome_and_Principe",
                            "Cape_Verde" = "Cabo_Verde",
                            "Dominican_Rep" = "Dominican_Republic"
                            
                            ))
```




```{r}
sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- left_join(sdg_report_classifier_data_missRanger_sdg_indicators, isolation, by = "geo_area_name")

sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>% 
  select(geo_area_name, ISOL)

# Timor Leste - 575
# Dominica - 568

sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>%                               # Replacing values
  mutate(ISOL = replace(ISOL, geo_area_name == "Dominica", 568))

sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>%                               # Replacing values
  mutate(ISOL = replace(ISOL, geo_area_name == "Timor-Leste", 575))

```


```{r}
# sdg_report_classifier_data_missRanger_sdg_indicators_isolation <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>% 
#   remove_rownames %>% 
#   column_to_rownames(var="geo_area_name")
```



```{r}
sdg_actual_classifier_data <- sdg_report_classifier_data_missRanger_sdg_indicators_isolation %>% 
  select(geo_area_name, 
goal_1_dash,
goal_2_dash,
goal_3_dash,
goal_4_dash,
goal_5_dash,
goal_6_dash,
goal_7_dash,
goal_8_dash,
goal_9_dash,
goal_10_dash,
goal_11_dash,
goal_12_dash,
goal_13_dash,
goal_14_dash,
goal_15_dash,
goal_16_dash,
goal_17_dash)
```

```{r}
# sdg_actual_classifier_data <- sdg_actual_classifier_data %>%
#   remove_rownames %>%
#   column_to_rownames(var="geo_area_name")
```



```{r}
# sdg_actual_classifier_data <- t(sdg_actual_classifier_data)
# 
# sdg_actual_classifier_data <- as.data.frame(sdg_actual_classifier_data)
# 
# sdg_actual_classifier_matrix<- as.matrix(sdg_actual_classifier_data)
```

```{r}
sdg_actual_classifier_data_longer <- sdg_actual_classifier_data %>% 
  pivot_longer(! geo_area_name, names_to = "Color", values_to = "Count")
```





```{r}
tile <- ggplot(sdg_actual_classifier_data_longer, 
       aes(x = geo_area_name,
           y = Color, 
           fill = Count)) + 
  geom_tile(show.legend = FALSE) +
  coord_flip() +
  scale_fill_manual(values = c("#20854EFF", "#80796BFF", "#CC8214FF", "#A73030FF", "#EFC000FF" )) +
  theme(axis.text.x = element_text(angle = 45,  hjust=1)) 

ggplotly(tile)
```




```{r}
sdg_actual_classifier_data_longer_all <- tibble::rownames_to_column(sdg_actual_classifier_data, "goal")
sdg_actual_classifier_data_longer_all <- tibble::column_to_rownames(sdg_actual_classifier_data, var = "rowname")
```



```{r}
sdg_actual_classifier_data_longer <- sdg_actual_classifier_data_longer %>% 
  pivot_longer(! goal, names_to = "Color", values_to = "Count")
  
```



```{r}
sdg_actual_classifier_data <- sdg_actual_classifier_data %>% 
  mutate(green_count = apply(sdg_actual_classifier_data, 1, function(x) length(which(x=="green"))))


sdg_actual_classifier_data <- sdg_actual_classifier_data %>% 
  mutate(red_count = apply(sdg_actual_classifier_data, 1, function(x) length(which(x=="red"))))

sdg_actual_classifier_data <- sdg_actual_classifier_data %>% 
  mutate(yellow_count = apply(sdg_actual_classifier_data, 1, function(x) length(which(x=="yellow"))))

sdg_actual_classifier_data <- sdg_actual_classifier_data %>% 
  mutate(orange_count = apply(sdg_actual_classifier_data, 1, function(x) length(which(x=="orange"))))

sdg_actual_classifier_data <- sdg_actual_classifier_data %>% 
  mutate(grey_count = apply(sdg_actual_classifier_data, 1, function(x) length(which(x=="grey"))))
```

```{r}
sdg_actual_classifier_data_longer <- sdg_actual_classifier_data %>% 
  select(green_count,
         yellow_count, 
         orange_count,
         red_count,
         grey_count)
```

```{r}
sdg_actual_classifier_data_longer <- tibble::rownames_to_column(sdg_actual_classifier_data_longer, "goal")
```



```{r}
sdg_actual_classifier_data_longer <- sdg_actual_classifier_data_longer %>% 
  pivot_longer(! goal, names_to = "Color", values_to = "Count")
  
```


```{r}
ggplot(data = sdg_actual_classifier_data_longer, aes(fill = Color, 
                                                     y = goal, 
                                                     x = Count)) + 
  geom_col(stat = 'identity') + 
  theme_bw() +
  scale_fill_manual(values = c("#20854EFF", "#80796BFF", "#CC8214FF", "#A73030FF", "#EFC000FF" ))
```
