---
title: "goal2_clean_summarise"
author: "Connor Flynn"
date: "7/21/2022"
output: html_document
---

Goal: The goal of this Rmd is to clean and summarize the data on Sustainable Development Goal 2.


## Load Libraries

The code chunk below reads in packages and functions used in this workflow:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                dplyr)

options(scipen = 99)
```


Import data

Each sustainable development goal (sdg) has it's own csv in the 'data' folder. 


Goal 2
```{r}
goal2 <- read_csv(here("data/sdg_data/Goal2.csv"))

```

This is all the indicator data for Sustainable Development Goal 2 for SIDS.

When we first import the data, we can see:
  - There are multiple observations for one country and the same indicator. 
      - This is to account for differences in data by year, age, sex, and geographic context for the same country.
      - This is a great idea, *however*, an extremely significant amount of the data is NA with this specific scope. 
  - We want the most recent picture of sustainable development goal measures for SIDS with as little NA values as possible, so:
      - We we summarize the data by taking the most recent year of data available for each SIDS and the mean value of age, sex, and urban vs rural geography for that year. 
      - This allows us to
        - Have as recent of a dataset as possible with as little NA values as possible, although the number of NA's is still significant
        - Keep the data frame to one SIDS per row and one sdg indicator per column.
      
Let's start cleaning:



Convert Value Column to class numeric in order to perform functions on the Value Column
```{r}
goal2 <- goal2 %>% 
  mutate(Value = as.numeric(Value))
```


The data has both NA and nan values so convert all missing data to NA

```{r}
goal2 <- goal2 %>% 
  mutate_all(~ifelse(is.nan(.), NA, .))

```


Drop NA values
```{r}
goal2 <- goal2 %>% 
  drop_na(Value)
```



Eliminate Spaces from SIDS Names and Series Descriptions (indicators)
```{r}
goal2$GeoAreaName <- gsub(" ", "_", goal2$GeoAreaName)

goal2$SeriesDescription <- gsub(" ", "_", goal2$SeriesDescription)
```


Look at Series Descriptions
```{r}
unique(goal2$SeriesDescription)
```

Group in order to get mean value from multiple categories of data for the same year
```{r}

goal2_tidy_grouped <- goal2 %>% 
  group_by(SeriesDescription, GeoAreaName, TimePeriod) %>% 
  summarise(Value = mean(Value, na.rm = TRUE))
```

Select the data point with the most recent year for each SIDS and Indicator
```{r}
goal2_tidy_grouped_most_recent <- goal2_tidy_grouped %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  slice(which.max(TimePeriod))
```

Drop time period to pivot_wider in next step
```{r}
goal2_tidy_grouped_most_recent_no_time <- goal2_tidy_grouped_most_recent %>% 
  select(!TimePeriod)
```

Pivot data to get one SIDS per row and one indicator per column
```{r}
goal2_wider <- goal2_tidy_grouped_most_recent_no_time %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = Value)
```


Clean column names with the janitor package
```{r}
goal2_wider  <- goal2_wider  %>% 
  clean_names()

```



Write into a csv file to the most_recent_data folder

```{r}
write_csv(goal2_wider, here("./most_recent/data_cleaned_and_summarized/goal2_most_recent.csv"))
```


Plot most recent data 

```{r}
most_recent_data <- table(goal2_tidy_grouped_most_recent['TimePeriod'])

most_recent_data <- as.data.frame(most_recent_data)
```


```{r}
ggplot(data = most_recent_data, aes(x = Var1, y = Freq)) +
  geom_col()
```



