---
title: "goal1_clean_summarise"
author: "Connor Flynn"
date: "7/21/2022"
output: html_document
---

Goal: The goal of this Rmd is to clean and summarize the data on Sustainable Development Goal 1. 



## Load Libraries

The code chunk below reads in packages and functions used in this workflow:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                dplyr)

options(scipen = 99)
```


Import data

Each sustainable development goal (sdg) has it's own csv in the 'data' folder. 


Goal 1
```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```



This is all the indicator data for Sustainable Development Goal 1 for SIDS.

When we first import the data, we can see:
  - There are multiple observations for one country and the same indicator. 
      - This is to account for differences in data by year, age, sex, and geographic context for the same country.
      - This is a great idea, *however*, an extremely significant amount of the data is NA with this specific scope. 
  - We want the most recent picture of sustainable development goal measures for SIDS with as little NA values as possible, so:
      - We we summarize the data by taking the most recent year of data available for each SIDS and the mean value of age, sex, and urban vs rural geography for that year. 
      - This allows us to
        - Have as recent of a dataset as possible with as little NA values as possible, although the number of NA's is still significant
        - Keep the data frame to one SIDS per row and one sdg indicator per column.
      
Let's start cleaning:


Convert Value Column to class numeric in order to perform functions on the Value Column
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```


The data has both NA and nan values so convert all missing data to NA

```{r}
goal1$Value[is.nan(goal1$Value)]<-NA
```

Drop NA values - no na's for this goal
```{r}
# # goal1 <- goal_1 %>% 
#   drop_na(Value)
```


Eliminate Spaces from SIDS Names and Series Descriptions (indicators)
```{r}
goal1$GeoAreaName <- gsub(" ", "_", goal1$GeoAreaName)

goal1$SeriesDescription <- gsub(" ", "_", goal1$SeriesDescription)
```


Look at Series Descriptions
```{r}
unique(goal1$SeriesDescription)
```

Filter for natural disaster related indicators because:
  - Due to the nature of this data (disasters not occurring every year, and recovery taking many years) we want the most significant (highest) value for these indicators
  - This does introduce some bias, but captures significant natural disasters for each SIDS (if one event has occurred in the last 20 years and the data has been collected)
    


```{r}
goal1_natural_disaster <- goal1 %>% 
  filter(SeriesDescription == "Number_of_people_affected_by_disaster_(number)"                                                                                                                
| SeriesDescription == "Number_of_directly_affected_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                   
| SeriesDescription == "Number_of_injured_or_ill_people_attributed_to_disasters_(number)"                                                                                              
| SeriesDescription == "Number_of_missing_persons_due_to_disaster_(number)"                                                                                                            
| SeriesDescription == "Number_of_deaths_and_missing_persons_attributed_to_disasters_(number)"                                                                                         
| SeriesDescription == "Number_of_deaths_due_to_disaster_(number)"                                                                                                                     
| SeriesDescription == "Number_of_deaths_and_missing_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                  
| SeriesDescription == "Number_of_people_whose_damaged_dwellings_were_attributed_to_disasters_(number)"                                                                                
| SeriesDescription == "Number_of_people_whose_livelihoods_were_disrupted_or_destroyed,_attributed_to_disasters_(number)"                                                              
| SeriesDescription == "Number_of_people_whose_destroyed_dwellings_were_attributed_to_disasters_(number)"                                                                              
| SeriesDescription == "Direct_agriculture_loss_attributed_to_disasters_(current_United_States_dollars)"                                                                               
| SeriesDescription == "Direct_economic_loss_resulting_from_damaged_or_destroyed_critical_infrastructure_attributed_to_disasters_(current_United_States_dollars)"                      
| SeriesDescription == "Direct_economic_loss_attributed_to_disasters_(current_United_States_dollars)" )
```


Group in order to get the strongest disaster event on record for each SIDS
  - Some SIDS report zeroes for non disaster years and some don't, so the mean and median become biased
  - Taking the strongest disaster does not account for frequency of disaster events but does capture a metric to measure the most significant disaster events
  


Group by Indicator and Place and take the higest value for each SIDS  
```{r}

goal1_natural_disaster_tidy_grouped <- goal1_natural_disaster %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  slice(which.max(Value))
```

Drop the time period in order to pivot_wider in the next step
```{r}
goal1_natural_disaster_tidy_grouped_max_no_time <- goal1_natural_disaster_tidy_grouped %>% 
  select(!TimePeriod)
```


Drop all other columns outside of scope (mostly na)
```{r}
goal1_natural_disaster_tidy_grouped_max_no_time <- goal1_natural_disaster_tidy_grouped %>% 
  select(SeriesDescription, Value, GeoAreaName)
```


Pivot data to get one SIDS per row and one indicator per column
```{r}
goal1_natural_disaster_wider <- goal1_natural_disaster_tidy_grouped_max_no_time %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = Value)
```


Clean column names using the janitor package
```{r}
goal1_natural_disaster_wider <- goal1_natural_disaster_wider %>% 
  clean_names()
```


Now select for indicators unrelated to disasters because we will be taking the most recent data available for these indicators opposed to the highest value for the disaster indicators


```{r}
goal1_no_disaster <- goal1 %>% 
  filter(SeriesDescription != "Number_of_people_affected_by_disaster_(number)"                                                                                                                
    & SeriesDescription != "Number_of_directly_affected_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                     
    & SeriesDescription != "Number_of_injured_or_ill_people_attributed_to_disasters_(number)"                                                                                                
    & SeriesDescription != "Number_of_missing_persons_due_to_disaster_(number)"                                                                                                              
    & SeriesDescription != "Number_of_deaths_and_missing_persons_attributed_to_disasters_(number)"                                                                                           
    & SeriesDescription != "Number_of_deaths_due_to_disaster_(number)"                                                                                                                       
    & SeriesDescription != "Number_of_deaths_and_missing_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                    
    & SeriesDescription != "Number_of_people_whose_damaged_dwellings_were_attributed_to_disasters_(number)"                                                                                  
    & SeriesDescription != "Number_of_people_whose_livelihoods_were_disrupted_or_destroyed,_attributed_to_disasters_(number)"                                                                
    & SeriesDescription != "Number_of_people_whose_destroyed_dwellings_were_attributed_to_disasters_(number)"                                                                                
    & SeriesDescription != "Direct_agriculture_loss_attributed_to_disasters_(current_United_States_dollars)"                                                                                 
    & SeriesDescription != "Direct_economic_loss_resulting_from_damaged_or_destroyed_critical_infrastructure_attributed_to_disasters_(current_United_States_dollars)"                        
    & SeriesDescription != "Direct_economic_loss_attributed_to_disasters_(current_United_States_dollars)" )
```


Group in order to get mean value from multiple categories of data for the same year
```{r}

goal1_no_disaster_tidy_grouped <- goal1_no_disaster %>% 
  group_by(SeriesDescription, GeoAreaName, TimePeriod) %>% 
  summarise(Value = mean(Value, na.rm = TRUE))
```

Select the data point with the most recent year for each SIDS and Indicator
```{r}
goal1_no_disaster_tidy_grouped_max <- goal1_no_disaster_tidy_grouped %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  slice(which.max(TimePeriod))
```


Drop time period to pivot_wider in next step
```{r}
goal1_no_disaster_tidy_grouped_max_no_time <- goal1_no_disaster_tidy_grouped_max %>% 
  select(!TimePeriod)
```


Pivot data to get one SIDS per row and one indicator per column
```{r}
goal1_no_disaster_wider <- goal1_no_disaster_tidy_grouped_max_no_time %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = Value)
```


Clean column names with the janitor package
```{r}
goal1_no_disaster_wider <- goal1_no_disaster_wider %>% 
  clean_names()

```


Join natural disaster data with other indicator data
```{r}
goal1_wider_joined <- full_join(goal1_no_disaster_wider, goal1_natural_disaster_wider, by = "geo_area_name")
```


Write into a csv file to the most_recent_data folder

```{r}
write_csv(goal1_wider_joined, here("./most_recent/data_cleaned_and_summarized/goal1_most_recent.csv"))
```


Plot most recent data 

```{r}
most_recent_data <- table(goal1_no_disaster_tidy_grouped_max['TimePeriod'])

most_recent_data <- as.data.frame(most_recent_data)
```


```{r}
ggplot(data = most_recent_data, aes(x = Var1, y = Freq)) +
  geom_col()
```



Plot all data 

```{r}
all_data_by_year <- table(goal1['TimePeriod'])

all_data_by_year <- as.data.frame(all_data_by_year)
```


```{r}
ggplot(data = all_data_by_year, aes(x = Var1, y = Freq)) +
  geom_col()
```