---
title: "test_most_recent_data"
author: "Connor Flynn"
date: "7/21/2022"
output: html_document
---

## Load Libraries

The code chunk below reads in packages and functions used in this workflow:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse,
                here,
                janitor,
                dplyr)

options(scipen = 99)
```


Import data

Each sustainable development goal (sdg) has it's own csv in the 'data' folder. 


Goal 1
```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```


Convert Value Column to class numeric in order to perform the median() function on the Value Column
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```


The data has both NA and nan values so convert all missing data to NA

```{r}
goal1$Value[is.nan(goal1$Value)]<-NA
```


Eliminate Spaces from SIDS Names and Series Descriptions (indicators)
```{r}
goal1$GeoAreaName <- gsub(" ", "_", goal1$GeoAreaName)

goal1$SeriesDescription <- gsub(" ", "_", goal1$SeriesDescription)
```


Look at Series Descriptions
```{r}
unique(goal1$SeriesDescription)
```

Filter for natural disaster related indicators because:
  - Due to the nature of this data (disasters not occurring every year) we want the mean value for these indicators
    - The mean 


```{r}
goal1_natural_disaster <- goal1 %>% 
  filter(SeriesDescription == "Number_of_people_affected_by_disaster_(number)"                                                                                                                
| SeriesDescription == "Number_of_directly_affected_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                   
| SeriesDescription == "Number_of_injured_or_ill_people_attributed_to_disasters_(number)"                                                                                              
| SeriesDescription == "Number_of_missing_persons_due_to_disaster_(number)"                                                                                                            
| SeriesDescription == "Number_of_deaths_and_missing_persons_attributed_to_disasters_(number)"                                                                                         
| SeriesDescription == "Number_of_deaths_due_to_disaster_(number)"                                                                                                                     
| SeriesDescription == "Number_of_deaths_and_missing_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                  
| SeriesDescription == "Number_of_people_whose_damaged_dwellings_were_attributed_to_disasters_(number)"                                                                                
| SeriesDescription == "Number_of_people_whose_livelihoods_were_disrupted_or_destroyed,_attributed_to_disasters_(number)"                                                              
| SeriesDescription == "Number_of_people_whose_destroyed_dwellings_were_attributed_to_disasters_(number)"                                                                              
| SeriesDescription == "Direct_agriculture_loss_attributed_to_disasters_(current_United_States_dollars)"                                                                               
| SeriesDescription == "Direct_economic_loss_resulting_from_damaged_or_destroyed_critical_infrastructure_attributed_to_disasters_(current_United_States_dollars)"                      
| SeriesDescription == "Direct_economic_loss_attributed_to_disasters_(current_United_States_dollars)" )
```


Group in order to get the strongest disaster event on record for each SIDS
  - Some SIDS report zeroes for non disaster years and some don't, so the mean and median become biased
  - This doesn't account for frequency of storm events but does capture a metric to measure the most significant disaster events
```{r}

goal1_natural_disaster_tidy_grouped <- goal1_natural_disaster %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  slice(which.max(Value))
```


```{r}
goal1_natural_disaster_tidy_grouped_max_no_time <- goal1_natural_disaster_tidy_grouped %>% 
  select(!TimePeriod)
```

```{r}
goal1_natural_disaster_tidy_grouped_max_no_time <- goal1_natural_disaster_tidy_grouped %>% 
  select(SeriesDescription, Value, GeoAreaName)
```


```{r}
goal1_natural_disaster_wider <- goal1_natural_disaster_tidy_grouped_max_no_time %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = Value)
```

```{r}
goal1_natural_disaster_wider <- goal1_natural_disaster_wider %>% 
  clean_names()
```


Now select for indicators unrelated to disasters


```{r}
goal1_no_disaster <- goal1 %>% 
  filter(SeriesDescription != "Number_of_people_affected_by_disaster_(number)"                                                                                                                
    & SeriesDescription != "Number_of_directly_affected_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                     
    & SeriesDescription != "Number_of_injured_or_ill_people_attributed_to_disasters_(number)"                                                                                                
    & SeriesDescription != "Number_of_missing_persons_due_to_disaster_(number)"                                                                                                              
    & SeriesDescription != "Number_of_deaths_and_missing_persons_attributed_to_disasters_(number)"                                                                                           
    & SeriesDescription != "Number_of_deaths_due_to_disaster_(number)"                                                                                                                       
    & SeriesDescription != "Number_of_deaths_and_missing_persons_attributed_to_disasters_per_100,000_population_(number)"                                                                    
    & SeriesDescription != "Number_of_people_whose_damaged_dwellings_were_attributed_to_disasters_(number)"                                                                                  
    & SeriesDescription != "Number_of_people_whose_livelihoods_were_disrupted_or_destroyed,_attributed_to_disasters_(number)"                                                                
    & SeriesDescription != "Number_of_people_whose_destroyed_dwellings_were_attributed_to_disasters_(number)"                                                                                
    & SeriesDescription != "Direct_agriculture_loss_attributed_to_disasters_(current_United_States_dollars)"                                                                                 
    & SeriesDescription != "Direct_economic_loss_resulting_from_damaged_or_destroyed_critical_infrastructure_attributed_to_disasters_(current_United_States_dollars)"                        
    & SeriesDescription != "Direct_economic_loss_attributed_to_disasters_(current_United_States_dollars)" )
```


Group in order to get mean value form multiple categories of data for the same year
```{r}

goal1_no_disaster_tidy_grouped <- goal1_no_disaster %>% 
  group_by(SeriesDescription, GeoAreaName, TimePeriod) %>% 
  summarise(Value = mean(Value, na.rm = TRUE))
```


```{r}
goal1_no_disaster_tidy_grouped_max <- goal1_no_disaster_tidy_grouped %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  slice(which.max(TimePeriod))
```


```{r}
goal1_no_disaster_tidy_grouped_max_no_time <- goal1_no_disaster_tidy_grouped_max %>% 
  select(!TimePeriod)
```


```{r}
goal1_no_disaster_wider <- goal1_no_disaster_tidy_grouped_max_no_time %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = Value)
```

```{r}
goal1_no_disaster_wider <- goal1_no_disaster_wider %>% 
  clean_names()

```


```{r}
goal1_wider_joined <- full_join(goal1_no_disaster_wider, goal1_natural_disaster_wider, by = "geo_area_name")
```



Plot most recent data 

```{r}
most_recent_data <- table(goal1_no_disaster_tidy_grouped_max['TimePeriod'])

most_recent_data <- as.data.frame(most_recent_data)
```


```{r}
ggplot(data = most_recent_data, aes(x = Var1, y = Freq)) +
  geom_col()
```



Plot all data 

```{r}
all_data_by_year <- table(goal1['TimePeriod'])

all_data_by_year <- as.data.frame(all_data_by_year)
```


```{r}
ggplot(data = all_data_by_year, aes(x = Var1, y = Freq)) +
  geom_col()
```



Goal 2 

```{r}
goal2 <- read_csv(here("data/sdg_data/Goal2.csv"))

```


Convert Value Column to class numeric in order to perform the median() function on the Value Column
```{r}
goal2 <- goal2 %>%
  mutate(Value = as.numeric(Value))
```


The data has both NA and nan values so convert all missing data to NA

```{r}
goal2$Value[is.nan(goal2$Value)]<-NA
```


Eliminate Spaces from SIDS Names and Series Descriptions (indicators)
```{r}
goal2$GeoAreaName <- gsub(" ", "_", goal2$GeoAreaName)

goal2$SeriesDescription <- gsub(" ", "_", goal2$SeriesDescription)
```


```{r}
unique(goal2$SeriesDescription)
```


```{r}

```

