---
title: "heatmap_less_na"
author: "Connor Flynn"
date: "7/29/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(pheatmap)
library(here)

```


Define Function
```{r}
count_na <- function(x) sum(is.na(x))
```


Goal 1

Import data
```{r}
goal1 <- read_csv(here("data/sdg_data/Goal1.csv"))

```

Convert Value Column to class numeric
```{r}
goal1 <- goal1 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal1$Value[is.nan(goal1$Value)]<-NA
```


```{r}
goal1$GeoAreaName <- gsub(" ", "_", goal1$GeoAreaName)

goal1$SeriesDescription <- gsub(" ", "_", goal1$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal1_tidy_grouped <- goal1 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal1_wider <- goal1_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```


```{r}
goal1_wider <- goal1_wider[, which(colMeans(!is.na(goal1_wider)) > 0.4)]
```



```{r}
goal1_wider_na <- goal1_wider %>% 
  mutate(goal1_na = apply(., 1, count_na))
```

```{r}
goal1_wider_na <- goal1_wider_na %>% 
  mutate(goal1_na = goal1_na/ncol(goal1_wider))
```


```{r}
goal1_na <- goal1_wider_na %>% 
  select(GeoAreaName, goal1_na)
```



Goal 2 

Import data
```{r}
goal2 <- read_csv(here("data/sdg_data/Goal2.csv"))

```

Convert Value Column to class numeric
```{r}
goal2 <- goal2 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal2$Value[is.nan(goal2$Value)]<-NA
```

```{r}
goal2$GeoAreaName <- gsub(" ", "_", goal2$GeoAreaName)

goal2$SeriesDescription <- gsub(" ", "_", goal2$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}
goal2_tidy_grouped <- goal2 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal2_wider <- goal2_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```

```{r}
goal2_wider <- goal2_wider[, which(colMeans(!is.na(goal2_wider)) > 0.4)]
```

```{r}
goal2_wider_na <- goal2_wider %>% 
  mutate(goal2_na = apply(., 1, count_na))
```

```{r}
goal2_wider_na <- goal2_wider_na %>% 
  mutate(goal2_na = goal2_na/ncol(goal2_wider))
```

```{r}
goal2_na <- goal2_wider_na %>% 
  select(GeoAreaName, goal2_na)
```

Goal 3 

Import data
```{r}
goal3 <- read_csv(here("data/sdg_data/Goal3.csv"))

```

Convert Value Column to class numeric
```{r}
goal3 <- goal3 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal3$Value[is.nan(goal3$Value)]<-NA
```

```{r}
goal3$GeoAreaName <- gsub(" ", "_", goal3$GeoAreaName)

goal3$SeriesDescription <- gsub(" ", "_", goal3$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal3_tidy_grouped <- goal3 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal3_wider <- goal3_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```


```{r}
goal3_wider <- goal3_wider[, which(colMeans(!is.na(goal3_wider)) > 0.4)]
```


```{r}
goal3_wider_na <- goal3_wider %>% 
  mutate(goal3_na = apply(., 1, count_na))
```


```{r}
goal3_wider_na <- goal3_wider_na %>% 
  mutate(goal3_na = goal3_na/ncol(goal3_wider))
```


```{r}
goal3_na <- goal3_wider_na %>% 
  select(GeoAreaName, goal3_na)
```


Goal 4

Import data
```{r}
goal4 <- read_csv(here("data/sdg_data/Goal4.csv"))

```

Convert Value Column to class numeric
```{r}
goal4 <- goal4 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal4$Value[is.nan(goal4$Value)]<-NA
```


```{r}
goal4$GeoAreaName <- gsub(" ", "_", goal4$GeoAreaName)

goal4$SeriesDescription <- gsub(" ", "_", goal4$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal4_tidy_grouped <- goal4 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal4_wider <- goal4_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue) 


```

```{r}
goal4_wider <- goal4_wider[, which(colMeans(!is.na(goal4_wider)) > 0.4)]
```



```{r}
goal4_wider_na <- goal4_wider %>% 
  mutate(goal4_na = apply(., 1, count_na))
```


```{r}
goal4_wider_na <- goal4_wider_na %>% 
  mutate(goal4_na = goal4_na/ncol(goal4_wider))
```

```{r}
goal4_na <- goal4_wider_na %>% 
  select(GeoAreaName, goal4_na)
```

Goal 5 

Import data
```{r}
goal5 <- read_csv(here("data/sdg_data/Goal5.csv"))

```

Convert Value Column to class numeric
```{r}
goal5 <- goal5 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal5$Value[is.nan(goal5$Value)]<-NA
```


```{r}
goal5$GeoAreaName <- gsub(" ", "_", goal5$GeoAreaName)

goal5$SeriesDescription <- gsub(" ", "_", goal5$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal5_tidy_grouped <- goal5 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal5_wider <- goal5_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal5_wider <- goal5_wider[, which(colMeans(!is.na(goal5_wider)) > 0.4)]
```

```{r}
goal5_wider_na <- goal5_wider %>% 
  mutate(goal5_na = apply(., 1, count_na))
```


```{r}
goal5_wider_na <- goal5_wider_na %>% 
  mutate(goal5_na = goal5_na/ncol(goal5_wider))
```


```{r}
goal5_na <- goal5_wider_na %>% 
  select(GeoAreaName, goal5_na)
```


Goal 6

Import data
```{r}
goal6 <- read_csv(here("data/sdg_data/Goal6.csv"))

```

Convert Value Column to class numeric
```{r}
goal6 <- goal6 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal6$Value[is.nan(goal6$Value)]<-NA
```


```{r}
goal6$GeoAreaName <- gsub(" ", "_", goal6$GeoAreaName)

goal6$SeriesDescription <- gsub(" ", "_", goal6$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal6_tidy_grouped <- goal6 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal6_wider <- goal6_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal6_wider <- goal6_wider[, which(colMeans(!is.na(goal6_wider)) > 0.4)]
```

```{r}
goal6_wider_na <- goal6_wider %>% 
  mutate(goal6_na = apply(., 1, count_na))
```


```{r}
goal6_wider_na <- goal6_wider_na %>% 
  mutate(goal6_na = goal6_na/ncol(goal6_wider))
```


```{r}
goal6_na <- goal6_wider_na %>% 
  select(GeoAreaName, goal6_na)
```


Goal 7 

Import data
```{r}
goal7 <- read_csv(here("data/sdg_data/Goal7.csv"))

```

Convert Value Column to class numeric
```{r}
goal7 <- goal7 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal7$Value[is.nan(goal7$Value)]<-NA
```

```{r}
goal7$GeoAreaName <- gsub(" ", "_", goal7$GeoAreaName)

goal7$SeriesDescription <- gsub(" ", "_", goal7$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal7_tidy_grouped <- goal7 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal7_wider <- goal7_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal7_wider <- goal7_wider[, which(colMeans(!is.na(goal7_wider)) > 0.4)]
```


```{r}
goal7_wider_na <- goal7_wider %>% 
  mutate(goal7_na = apply(., 1, count_na))
```


```{r}
goal7_wider_na <- goal7_wider_na %>% 
  mutate(goal7_na = goal7_na/ncol(goal7_wider))
```



```{r}
goal7_na <- goal7_wider_na %>% 
  select(GeoAreaName, goal7_na)
```


Goal 8 

Import data
```{r}
goal8 <- read_csv(here("data/sdg_data/Goal8.csv"))

```

Convert Value Column to class numeric
```{r}
goal8 <- goal8 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal8$Value[is.nan(goal8$Value)]<-NA
```


```{r}
goal8$GeoAreaName <- gsub(" ", "_", goal8$GeoAreaName)

goal8$SeriesDescription <- gsub(" ", "_", goal8$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal8_tidy_grouped <- goal8 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal8_wider <- goal8_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)
```


```{r}
goal8_wider <- goal8_wider[, which(colMeans(!is.na(goal8_wider)) > 0.4)]
```


```{r}
goal8_wider_na <- goal8_wider %>% 
  mutate(goal8_na = apply(., 1, count_na))
```


```{r}
goal8_wider_na <- goal8_wider_na %>% 
  mutate(goal8_na = goal8_na/ncol(goal8_wider))
```


```{r}
goal8_na <- goal8_wider_na %>% 
  select(GeoAreaName, goal8_na)
```

Goal 9 

Import data
```{r}
goal9 <- read_csv(here("data/sdg_data/Goal9.csv"))

```

Convert Value Column to class numeric
```{r}
goal9 <- goal9 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal9$Value[is.nan(goal9$Value)]<-NA
```


```{r}
goal9$GeoAreaName <- gsub(" ", "_", goal9$GeoAreaName)

goal9$SeriesDescription <- gsub(" ", "_", goal9$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal9_tidy_grouped <- goal9 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal9_wider <- goal9_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```

```{r}
goal9_wider <- goal9_wider[, which(colMeans(!is.na(goal9_wider)) > 0.4)]
```


```{r}
goal9_wider_na <- goal9_wider %>% 
  mutate(goal9_na = apply(., 1, count_na))
```

```{r}
goal9_wider_na <- goal9_wider_na %>% 
  mutate(goal9_na = goal9_na/ncol(goal9_wider))
```


```{r}
goal9_na <- goal9_wider_na %>% 
  select(GeoAreaName, goal9_na)
```


Goal 10 

Import data
```{r}
goal10 <- read_csv(here("data/sdg_data/Goal10.csv"))

```

Convert Value Column to class numeric
```{r}
goal10 <- goal10 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal10$Value[is.nan(goal10$Value)]<-NA
```


```{r}
goal10$GeoAreaName <- gsub(" ", "_", goal10$GeoAreaName)

goal10$SeriesDescription <- gsub(" ", "_", goal10$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal10_tidy_grouped <- goal10 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal10_wider <- goal10_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal10_wider <- goal10_wider[, which(colMeans(!is.na(goal10_wider)) > 0.4)]
```


```{r}
goal10_wider_na <- goal10_wider %>% 
  mutate(goal10_na = apply(., 1, count_na))
```


```{r}
goal10_wider_na <- goal10_wider_na %>% 
  mutate(goal10_na = goal10_na/ncol(goal10_wider))
```


```{r}
goal10_na <- goal10_wider_na %>% 
  select(GeoAreaName, goal10_na)
```


Goal 11 

Import data
```{r}
goal11 <- read_csv(here("data/sdg_data/Goal11.csv"))

```

Convert Value Column to class numeric
```{r}
goal11 <- goal11 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal11$Value[is.nan(goal11$Value)]<-NA
```

```{r}
goal11$GeoAreaName <- gsub(" ", "_", goal11$GeoAreaName)

goal11$SeriesDescription <- gsub(" ", "_", goal11$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal11_tidy_grouped <- goal11 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm =TRUE))
```


```{r}
goal11_wider <- goal11_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```

```{r}
goal11_wider <- goal11_wider[, which(colMeans(!is.na(goal11_wider)) > 0.4)]
```

```{r}
goal11_wider_na <- goal11_wider %>% 
  mutate(goal11_na = apply(., 1, count_na))
```


```{r}
goal11_wider_na <- goal11_wider_na %>% 
  mutate(goal11_na = goal11_na/ncol(goal11_wider))
```

```{r}
goal11_na <- goal11_wider_na %>% 
  select(GeoAreaName, goal11_na)
```


Goal 12

Import data
```{r}
goal12 <- read_csv(here("data/sdg_data/Goal12.csv"))

```

Convert Value Column to class numeric
```{r}
goal12 <- goal12 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal12$Value[is.nan(goal12$Value)]<-NA
```

```{r}
goal12$GeoAreaName <- gsub(" ", "_", goal12$GeoAreaName)

goal12$SeriesDescription <- gsub(" ", "_", goal12$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal12_tidy_grouped <- goal12 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal12_wider <- goal12_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

```


```{r}
goal12_wider <- goal12_wider[, which(colMeans(!is.na(goal12_wider)) > 0.4)]
```



```{r}
goal12_wider_na <- goal12_wider %>% 
  mutate(goal12_na = apply(., 1, count_na))
```


```{r}
goal12_wider_na <- goal12_wider_na %>% 
  mutate(goal12_na = goal12_na/ncol(goal12_wider))
```


```{r}
goal12_na <- goal12_wider_na %>% 
  select(GeoAreaName, goal12_na)
```



Goal 13

Import data
```{r}
goal13 <- read_csv(here("data/sdg_data/Goal13.csv"))

```

Convert Value Column to class numeric
```{r}
goal13 <- goal13 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal13$Value[is.nan(goal13$Value)]<-NA
```

```{r}
goal13$GeoAreaName <- gsub(" ", "_", goal13$GeoAreaName)

goal13$SeriesDescription <- gsub(" ", "_", goal13$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal13_tidy_grouped <- goal13 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal13_wider <- goal13_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal13_wider <- goal13_wider[, which(colMeans(!is.na(goal13_wider)) > 0.4)]
```


```{r}
goal13_wider_na <- goal13_wider %>% 
  mutate(goal13_na = apply(., 1, count_na))
```


```{r}
goal13_wider_na <- goal13_wider_na %>% 
  mutate(goal13_na = goal13_na/ncol(goal13_wider))
```


```{r}
goal13_na <- goal13_wider_na %>% 
  select(GeoAreaName, goal13_na)
```


Goal 14 

Goal 14

Import data
```{r}
goal14 <- read_csv(here("data/sdg_data/Goal14.csv"))

```

Convert Value Column to class numeric
```{r}
goal14 <- goal14 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal14$Value[is.nan(goal14$Value)]<-NA
```


```{r}
goal14$GeoAreaName <- gsub(" ", "_", goal14$GeoAreaName)

goal14$SeriesDescription <- gsub(" ", "_", goal14$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal14_tidy_grouped <- goal14 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal14_wider <- goal14_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal14_wider <- goal14_wider[, which(colMeans(!is.na(goal14_wider)) > 0.4)]
```



```{r}
goal14_wider_na <- goal14_wider %>% 
  mutate(goal14_na = apply(., 1, count_na))
```


```{r}
goal14_wider_na <- goal14_wider_na %>% 
  mutate(goal14_na = goal14_na/ncol(goal14_wider))
```


```{r}
goal14_na <- goal14_wider_na %>% 
  select(GeoAreaName, goal14_na)
```



Goal 15 

Import data
```{r}
goal15 <- read_csv(here("data/sdg_data/Goal15.csv"))

```

Convert Value Column to class numeric
```{r}
goal15 <- goal15 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal15$Value[is.nan(goal15$Value)]<-NA
```

```{r}
goal15$GeoAreaName <- gsub(" ", "_", goal15$GeoAreaName)

goal15$SeriesDescription <- gsub(" ", "_", goal15$SeriesDescription)
```


Group in order to get median value form multiple years/categories of data
```{r}

goal15_tidy_grouped <- goal15 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal15_wider <- goal15_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)

```


```{r}
goal15_wider <- goal15_wider[, which(colMeans(!is.na(goal15_wider)) > 0.4)]
```


```{r}
goal15_wider_na <- goal15_wider %>% 
  mutate(goal15_na = apply(., 1, count_na))
```


```{r}
goal15_wider_na <- goal15_wider_na %>% 
  mutate(goal15_na = goal15_na/ncol(goal15_wider))
```


```{r}
goal15_na <- goal15_wider_na %>% 
  select(GeoAreaName, goal15_na)
```




Goal 16 

Import data
```{r}
goal16 <- read_csv(here("data/sdg_data/Goal16.csv"))

```

Convert Value Column to class numeric
```{r}
goal16 <- goal16 %>% 
  mutate(Value = as.numeric(Value))
```


```{r}
goal16$Value[is.nan(goal16$Value)]<-NA
```


```{r}
goal16$GeoAreaName <- gsub(" ", "_", goal16$GeoAreaName)

goal16$SeriesDescription <- gsub(" ", "_", goal16$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal16_tidy_grouped <- goal16 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal16_wider <- goal16_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal16_wider <- goal16_wider[, which(colMeans(!is.na(goal16_wider)) > 0.4)]
```


```{r}
goal16_wider_na <- goal16_wider %>% 
  mutate(goal16_na = apply(., 1, count_na))
```


```{r}
goal16_wider_na <- goal16_wider_na %>% 
  mutate(goal16_na = goal16_na/ncol(goal16_wider))
```


```{r}
goal16_na <- goal16_wider_na %>% 
  select(GeoAreaName, goal16_na)
```


Goal 17


Import data
```{r}
goal17 <- read_csv(here("data/sdg_data/Goal17.csv"))

```

Convert Value Column to class numeric
```{r}
goal17 <- goal17 %>% 
  mutate(Value = as.numeric(Value))
```

```{r}
goal17$Value[is.nan(goal17$Value)]<-NA
```

```{r}
goal17$GeoAreaName <- gsub(" ", "_", goal17$GeoAreaName)

goal17$SeriesDescription <- gsub(" ", "_", goal17$SeriesDescription)
```

Group in order to get median value form multiple years/categories of data
```{r}

goal17_tidy_grouped <- goal17 %>% 
  group_by(SeriesDescription, GeoAreaName) %>% 
  summarise(MedianValue = median(Value, na.rm = TRUE))
```


```{r}
goal17_wider <- goal17_tidy_grouped %>% 
  pivot_wider(names_from = SeriesDescription,
              values_from = MedianValue)


```


```{r}
goal17_wider <- goal17_wider[, which(colMeans(!is.na(goal17_wider)) > 0.4)]
```


```{r}
goal17_wider_na <- goal17_wider %>% 
  mutate(goal17_na = apply(., 1, count_na))
```


```{r}
goal17_wider_na <- goal17_wider_na %>% 
  mutate(goal17_na = goal17_na/ncol(goal17_wider))
```


```{r}
goal17_na <- goal17_wider_na %>% 
  select(GeoAreaName, goal17_na)
```


Join 


```{r}
goal1_2 <- full_join(goal1_na, goal2_na)
goal1_3 <- full_join(goal1_2, goal3_na)
goal1_4 <- full_join(goal1_3, goal4_na)
goal1_5 <- full_join(goal1_4, goal5_na)
goal1_6 <- full_join(goal1_5, goal6_na)
goal1_7 <- full_join(goal1_6, goal7_na)
goal1_8 <- full_join(goal1_7, goal8_na)
goal1_9 <- full_join(goal1_8, goal9_na)
goal1_10 <- full_join(goal1_9, goal10_na)
goal1_11 <- full_join(goal1_10, goal11_na)
goal1_12 <- full_join(goal1_11, goal12_na)
goal1_13 <- full_join(goal1_12, goal13_na)
goal1_14 <- full_join(goal1_13, goal14_na)
goal1_15 <- full_join(goal1_14, goal15_na)
goal1_16 <- full_join(goal1_15, goal16_na)
goal1_17 <- full_join(goal1_16, goal17_na)

sdg_na_percentages_joined <- goal1_17
```



```{r}
write_csv(sdg_na_percentages_joined, here("na_analysis/data/sdg_na_percentages_joined.csv"))
```

Visualize 

```{r}
sdg_na_percentages_joined <- sdg_na_percentages_joined %>% 
  remove_rownames %>% 
  column_to_rownames(var="GeoAreaName")
```


```{r}
sdg_na_percentages_matrix <- data.matrix(sdg_na_percentages_joined)
```




```{r}
f <- pheatmap(sdg_na_percentages_matrix, treeheight_row = 0, treeheight_col = 0, display_numbers = TRUE, fontsize_number = 6, angle_col = 45, na_col = "red", main = "Missing SDG Data for SIDS, (measured in % of Missing Data per Goal)")
```